---
title: "environmenal/exploratory analysis"
output: html_document
date: "2022-11-06"
---

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
#library(raster)
library(terra)
library(PAMpal)
library(PAMmisc)
#library(marmap)
library(rerddap)
```

### Get Environmental Variables

For each buoy, the value of each environmental variable will be added to each track point based on Lat, Long, and UTC.
Data only need to be downloaded once. After that, can refer to the file in the external hard drive ("D:").

Environmental variables: Sea surface temp, Wind stress curl, Distance to continental slope, Depth, bathymetric slope,
distance to shore, chlorophyll, sea surface height anomalies, + Hycom variables.

Sea Surface Temperature from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST07", var = c('analysed_sst'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST08", var = c('analysed_sst'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST10", var = c('analysed_sst'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST12", var = c('analysed_sst'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST13", var = c('analysed_sst'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST14", var = c('analysed_sst'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST16", var = c('analysed_sst'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST18", var = c('analysed_sst'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST19", var = c('analysed_sst'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST20", var = c('analysed_sst'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST21", var = c('analysed_sst'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST22", var = c('analysed_sst'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST23", var = c('analysed_sst'))
```

Once downloaded, matches SST from file
```{r}
SSTlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="analysedSST")

for (ss in SSTlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ss, 33, 34))), nc = ss) %>%
  rename(., sst_mean = analysed_sst_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)   # rename new column to "sst_mean" and remove unnecessary columns

  assign(paste0("tracks_SS_", substr(ss, 33, 34)), data)
}
```
### Wind Stress Curl from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress07.nc", var = c('curl'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress08.nc", var = c('curl'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress10.nc", var = c('curl'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress12.nc", var = c('curl'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress13.nc", var = c('curl'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress14.nc", var = c('curl'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress16.nc", var = c('curl'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress18.nc", var = c('curl'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress19.nc", var = c('curl'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress20.nc", var = c('curl'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress21.nc", var = c('curl'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress22.nc", var = c('curl'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress23.nc", var = c('curl'))

# Pulls from downloaded file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data-raw/erdQMstress1day_LonPM180.nc')
#tracks_SS_08

#windcurl <- erddapToEdinfo('erdQMstress1day', baseurl = 'https://coastwatch.pfeg.noaa.gov/erddap/')

#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc=windcurl, fileName='windcurl.nc')

```
Once downloaded, matches wind stress curl from file
```{r}
windlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="windstress")

for (w in windlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(w, 32, 33))), nc = w) %>%
     dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean, -matchDepth_mean)   # remove unnecessary columns
  
  assign(paste0("tracks_SS_", substr(w, 32, 33)), data)
}
```

### Distance to continental slope (uses terra package)
```{r}
bathy <- rast("D:/CCES_gebco_bathy.tif") # Bathymetry for all of CCE from https://download.gebco.net/
agg <- terra::aggregate(bathy, 5)  # Increase cell size by factor of 5 to be visible

cont <- st_as_sf(as.contour(bathy, )) # Create contour lines from bathymetry 
cont_slope <- cont %>% filter(level == -2000) # Establish continental shelf. Is 2000m the correct depth for continental shelf?

tracklist <- grep(pattern = "tracks_SS_", names(.GlobalEnv), value = T)

for (t in tracklist) {
  sf <- st_as_sf(get(t), coords = c("Longitude", "Latitude"), crs=4326, remove=F)
  trk <- terra::rasterize(vect(sf), agg)
  slop <- terra::distance(trk, vect(cont_slope))
  ext <- terra::extract(slop, vect(sf))
  
  dbind <- cbind(sf, ext) %>%
  dplyr::select(-ID) %>%
  rename("dist2slope" = last) %>%
  st_set_geometry(NULL) # remove geometry to prevent buoy dataframe from becoming sf object for future 
  
  assign(paste0("tracks_SS_", substr(t, 11, 12)), dbind)
}
```

Depth from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth07.nc", var = c('z'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth08.nc", var = c('z'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth10.nc", var = c('z'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth12.nc", var = c('z'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth13.nc", var = c('z'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth14.nc", var = c('z'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth16.nc", var = c('z'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth18.nc", var = c('z'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth19.nc", var = c('z'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth20.nc", var = c('z'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth21.nc", var = c('z'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth22.nc", var = c('z'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth23.nc", var = c('z'))
```

Once downloaded, matches depth from file
```{r}
depthlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="depth")

for (dd in depthlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(dd, 27, 28))), nc = dd) %>%
  rename(., depth = z_mean) %>%        # rename new column to "depth"
  mutate(depth = depth*-1) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(dd, 27, 28)), data)
}
```

#### Bathymetric slope (skipping loop for now)
```{r}
bathy_slope <- terra::terrain(bathy, v = "slope")

for (t in tracklist) {
  slope <- terra::extract(bathy_slope, get(t)[,4:3]) %>%  # Reads latitude and longitude of buoy dataframe
  dplyr::select(-ID) %>%
  rename("bathy_slope" = slope)
  
  sbind <- cbind(get(t), slope)
  
  assign(paste0("tracks_SS_", substr(t, 11, 12)), sbind)
}
```

Distance to Shore from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore07.nc", var = c('dist'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore08.nc", var = c('dist'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore10.nc", var = c('dist'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore12.nc", var = c('dist'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore13.nc", var = c('dist'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore14.nc", var = c('dist'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore16.nc", var = c('dist'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore18.nc", var = c('dist'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore19.nc", var = c('dist'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore20.nc", var = c('dist'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore21.nc", var = c('dist'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore22.nc", var = c('dist'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore23.nc", var = c('dist'))
```

Once downloaded, matches Distance to Shore from file
```{r}
distlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="dist2shore")

for (d2 in distlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(d2, 32, 33))), nc = d2) %>%
  rename(., dist2shore = dist_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(d2, 32, 33)), data)
}
```

### Chlorophyll from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll07.nc", var = c('chlorophyll'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll08.nc", var = c('chlorophyll'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll10.nc", var = c('chlorophyll'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll12.nc", var = c('chlorophyll'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll13.nc", var = c('chlorophyll'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll14.nc", var = c('chlorophyll'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll16.nc", var = c('chlorophyll'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll18.nc", var = c('chlorophyll'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll19.nc", var = c('chlorophyll'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll20.nc", var = c('chlorophyll'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll21.nc", var = c('chlorophyll'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll22.nc", var = c('chlorophyll'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll23.nc", var = c('chlorophyll'))
```

Once downloaded, matches chlorophyll from file
```{r}
chlalist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="chlorophyll")

for (ch in chlalist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ch, 33, 34))), nc = ch) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(ch, 33, 34)), data)
}
```

Sea Surface Height Anomalies from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh07.nc", var = c('sla'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh08.nc", var = c('sla'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh10.nc", var = c('sla'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh12.nc", var = c('sla'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh13.nc", var = c('sla'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh14.nc", var = c('sla'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh16.nc", var = c('sla'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh18.nc", var = c('sla'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh19.nc", var = c('sla'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh20.nc", var = c('sla'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh21.nc", var = c('sla'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh22.nc", var = c('sla'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh23.nc", var = c('sla'))
```

Once downloaded, matches sea surface height anomalies from file
```{r}
sshlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="ssh")

for (sh in sshlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(sh, 25, 26))), nc = sh) %>%
  rename(., ssh_mean = sla_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(sh, 25, 26)), data)
}
```


#### HyCOM Data - MLDepth, MLTemp, TTemp, TDepth, Salinity

Create function to estimate thermocline variables using the temperature at depth data
```{r}
calcThermoVars <- function(depth, temp, mldMode='SST8', thermMode='variso', plot=FALSE) {
    # depthInterp <- approxfun(x=temp, y=depth)
    switch(match.arg(mldMode),
           'SST8' = {
               mldTemp <- temp[1] - 0.8
               # first few temps are likely to have repeat values that trigger
               # warnings for approxfun, so cut off to only values after mldTemp
               useMin <- min(which(temp <= mldTemp)) - 1
               useIx <- useMin:length(temp)
               depthInterp <- approxfun(x=temp[useIx], y=depth[useIx])
               mld <- depthInterp(mldTemp)
           }
    )
    switch(match.arg(thermMode),
           'variso' = {
               t400 <- approx(x=depth, y=temp, xout=400)$y
               # therm end is half way to t400 temp
               tEnd <- mldTemp + (t400 - mldTemp)/2
               # therm temp is midpt from mld to end
               tt <- (mldTemp + tEnd)/2
               # tt <- mldTemp - .25 * (mldTemp - t400)
               ttDepth <- depthInterp(tt)
               tEndDepth <- depthInterp(tEnd)
           }
    )
    if(plot) {
        to300 <- depth <= 300
        plot(x=temp[to300], y=-depth[to300],
             main = paste0('MixLayer: ', round(mld,0), 'm ', round(mldTemp, 1), 'C',
                           '\nTherm: ', round(ttDepth, 0), 'm ', round(tt, 1), 'C'),
             xlab='Temp (C)', ylab='Depth (m)')
        
        lines(x=temp[to300], y=-depth[to300])
        lines(x=c(mldTemp, tEnd), y=c(-mld, -tEndDepth), col='darkgray', lwd=4)
        points(x=c(mldTemp, tt), y=c(-mld, -ttDepth), col='blue', cex=1.5, pch=15)
    }
    list(mldDepth = mld, mldTemp = mldTemp,
         ttDepth = ttDepth, ttTemp = tt)
}
```


```{r}
# Create loop for each buoy to download HYCOM data

##FIX THIS - try testing on ONE buoy
for (t in tracklist) {
  Hdata <- matchEnvData(as.data.frame(get(paste0("tracks_SS_", substr(t, 11, 12)))), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)
  
  thermData <- bind_rows(lapply(Hdata, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))
  bindr <- cbind(get(paste0("tracks_SS_", substr(t, 11, 12))), thermData)
  assign(paste0("tracks_SS_", substr(t, 11, 12)), bindr) #fix this part?
}
```

```{r}
test08 <- matchEnvData(as.data.frame(tracks_SS_08), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

thermData08 <- bind_rows(lapply(test08, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

tracks_SS_08 <- cbind(tracks_SS_08, thermData08)
```


```{r}
#hycomData0 <- matchEnvData(as.data.frame(tracks_SS_08[1:250,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm0.nc")

#test <- matchEnvData(as.data.frame(tracks_SS_07), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)


#hycomData1 <- matchEnvData(as.data.frame(tracks_SS_08[251:500,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm1.nc")

#hycomData2 <- matchEnvData(as.data.frame(tracks_SS_08[501:750,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm2.nc")

#hycomData3 <- matchEnvData(as.data.frame(tracks_SS_08[751:1200,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm3.nc")

#hycomData4 <- matchEnvData(as.data.frame(tracks_SS_08[1201:1500,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm4.nc")

#hycomData5 <- matchEnvData(as.data.frame(tracks_SS_08[1501:1800,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm5.nc")

#hycomData6 <- matchEnvData(as.data.frame(tracks_SS_08[1801:2145,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm6.nc")

#hycomData7 <- matchEnvData(as.data.frame(tracks_SS_08[2146:2469,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm7.nc")

#hycomData8 <- matchEnvData(as.data.frame(tracks_SS_08[2470:2769,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm8.nc")


# Run the 9 nc lists that make up tracks_SS_08
#hycomData0 <- matchEnvData(as.data.frame(tracks_SS_08[1:250,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm0.nc")
#hycomData1 <- matchEnvData(as.data.frame(tracks_SS_08[251:500,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm1.nc")
#hycomData2 <- matchEnvData(as.data.frame(tracks_SS_08[501:750,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm2.nc")
#hycomData3 <- matchEnvData(as.data.frame(tracks_SS_08[751:1200,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm3.nc")
#hycomData4 <- matchEnvData(as.data.frame(tracks_SS_08[1201:1500,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm4.nc")
#hycomData5 <- matchEnvData(as.data.frame(tracks_SS_08[1501:1800,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm5.nc")
#hycomData6 <- matchEnvData(as.data.frame(tracks_SS_08[1801:2145,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm6.nc")
#hycomData7 <- matchEnvData(as.data.frame(tracks_SS_08[2146:2469,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm7.nc")
#hycomData8 <- matchEnvData(as.data.frame(tracks_SS_08[2470:2769,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "data-raw/hycomm8.nc")
```


Use above function on the smaller hycom datasets (0-6)
```{r}
#Optional plot:
calcThermoVars(test[[1]]$matchDepth, test[[1]]$water_temp, plot=TRUE)

thermData0 <- bind_rows(lapply(hycomData0, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData1 <- bind_rows(lapply(hycomData1, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData2 <- bind_rows(lapply(hycomData2, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData3 <- bind_rows(lapply(hycomData3, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData4 <- bind_rows(lapply(hycomData4, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData5 <- bind_rows(lapply(hycomData5, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData6 <- bind_rows(lapply(hycomData6, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData7 <- bind_rows(lapply(hycomData7, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

thermData8 <- bind_rows(lapply(hycomData8, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

# Bind all thermocline datasets together
thermData <- rbind(thermData0, thermData1, thermData2, thermData3, thermData4, 
                   thermData5, thermData6, thermData7, thermData8)

# Bind main thermocline dataset to main track/soundscape dataframe
tracks_SS_08 <- cbind(tracks_SS_08, thermData)

# New tracks_SS_08 variable contains Hycom variables now
##### FINAL tracks_ss_08 dataframe ######
View(tracks_SS_08)
```
```{r}
thermData <- bind_rows(lapply(test, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

test_fin <- cbind(tracks_SS_07, thermData)
print(data)
```
testing hycom bind on ONE drift first
```{r}
test22 <- matchEnvData(as.data.frame(tracks_SS_22), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

thermData22 <- bind_rows(lapply(test22, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

test_fin <- cbind(tracks_SS_22, thermData22)
View(test_fin)
```

```{r}
saveRDS(tracks_SS_10, 'data/fulltrack10.rda')
saveRDS(tracks_SS_12, 'data/fulltrack12.rda')
saveRDS(tracks_SS_13, 'data/fulltrack13.rda')
saveRDS(tracks_SS_14, 'data/fulltrack14.rda')
saveRDS(tracks_SS_16, 'data/fulltrack16.rda')
saveRDS(tracks_SS_18, 'data/fulltrack18.rda')
saveRDS(tracks_SS_19, 'data/fulltrack19.rda')
saveRDS(tracks_SS_20, 'data/fulltrack20.rda')
saveRDS(tracks_SS_21, 'data/fulltrack21.rda')
saveRDS(tracks_SS_22, 'data/fulltrack22.rda')
saveRDS(tracks_SS_23, 'data/fulltrack23.rda')
saveRDS(tracks_SS_07, 'data/fulltrack07.rda')
saveRDS(tracks_SS_08, 'data/fulltrack08.rda')
```


Get avg daily environmental variables
```{r}
means_08 <- tracks_SS_08 %>%
  group_by(as.Date(UTC))%>%
  summarize(sst_mean = mean(sst_mean),
            dist_slope = mean(dist2slope),
            depth = mean(depth),
            slope = mean(slope),
            dist_shore = mean(dist2shore),
            chlorophyll_mean = mean(chlorophyll_mean),
            ssh_mean = mean(ssh_mean),
            mldDepth = mean(mldDepth),
            mldTemp = mean(mldTemp),
            ttDepth = mean(ttDepth),
            ttTemp = mean(ttTemp),
            temp400 = mean(temp400),
            sal400 = mean(sal400),
            BWpresence = sum(BWpresence))
```

### Exploratory Analysis ######

### Third octave levels histograms

```{r}
# Drift 8 - all TOL bands, facet wrap
pivot <- tracks_SS_08 %>%
  pivot_longer(cols = starts_with("TOL") | starts_with("BB"), names_to = "SL", values_to = "Hz")    # Pivot longer for histogram facet grid

ggplot(data = pivot, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 3, color = "black") +
  theme_classic() +
  ggtitle("Distribution of third octave level intensities: Drift 8") +
  labs(x = "Sound Intensity (dB)") +
  guides(fill = guide_legend(title = "Beaked Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.7,0.8)) +
  facet_grid(~SL)

# Drift 10 - all TOL bands, facet grid
pivot2 <- tracks_SS_10 %>%
  pivot_longer(cols = starts_with("TOL")| starts_with("BB"), names_to = "SL", values_to = "Hz")    # Pivot longer for histogram facet grid

ggplot(data = pivot2, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 3, color = "black") +
  theme_classic() +
  ggtitle("Distribution of third octave level intensities: Drift 10") +
  scale_x_continuous(name = "Sound Intensity (dB)", breaks=seq(50,110,20)) +
  guides(fill = guide_legend(title = "Beaked Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.6,0.76)) +
  facet_grid(~SL)
  
# Drift 8 - TOL bands 125 and 2000 only
pivot3 <- tracks_SS_08 %>%
  dplyr::select(-TOL_63, -TOL_20000, -TOL_5000) %>%
  pivot_longer(cols = starts_with("TOL"), names_to = "TOL", values_to = "Hz")    # Pivot longer for histogram facet grid

TOL.labs <- c(`TOL_125` = "TOL at 125 Hz", 
              `TOL_2000` = "TOL at 2000 Hz")
```

```{r drift-8-histogram}
ggplot(data = pivot3, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 1, color = "black") +
  theme_classic() +
  ggtitle("Distribution of Third-Octave Level (TOL) Intensities: Buoy 8") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_manual(name = "Beaked Whale Presence", 
                    labels = c("0" = "Absent", "1" = "Present"),
                    values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.6,0.7)) +
  facet_wrap(~TOL, labeller = as_labeller(TOL.labs))
```


```{r}
# Drift 10 - TOL bands 125 and 2000 only
pivot4 <- tracks_SS_10 %>%
  dplyr::select(-TOL_63, -TOL_20000, -TOL_5000) %>%
  pivot_longer(cols = starts_with("TOL"), names_to = "TOL", values_to = "Hz")    # Pivot longer for histogram facet grid


ggplot(data = pivot4, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 1, color = "black") +
  theme_classic() +
  ggtitle("Distribution of Third-Octave Level (TOL) Intensities: Buoy 10") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_manual(name = "Beaked Whale Presence", 
                    labels = c("0" = "Absent", "1" = "Present"),
                    values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.6,0.7)) +
  facet_wrap(~TOL, labeller = as_labeller(TOL.labs))

TOL.labs <- c(`TOL_125` = "TOL at 125 Hz", 
              `TOL_2000` = "TOL at 2000 Hz")
```



Scatterplots

```{r}
# SST vs TOL 2000
ggplot(data = tracks_SS_08, aes(x = sst_mean, y = `TOL_2000`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# SST over time
ggplot(tracks_SS_08, aes(x = UTC, y = sst_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")


# Depth vs TOL 125
ggplot(data = tracks_SS_08, aes(x = depth, y = `TOL_125`)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

#Mean depth over time
ggplot(means_08, aes(x = `as.Date(UTC)`, y = depth*(-1))) +
  geom_line()

# Chlorophyll vs TOL 125
ggplot(data = tracks_SS_08, aes(x = chlorophyll_mean, y = `TOL_125`)) +
  geom_point(aes(color = species))

# CHl over time
ggplot(tracks_SS_08, aes(x = UTC, y = chlorophyll_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")

# Mixed Layer Depth vs TOL125 with species
ggplot(data = tracks_SS_08, aes(x = mldDepth, y = `TOL_125`)) +
  geom_point(aes(color = species))

# Mixed Layer Depth over time
ggplot(tracks_SS_08, aes(x = UTC, y = mldDepth*(-1))) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

ggplot(data = tracks_SS_08, aes(x = slope, y = `TOL_5000`)) +
  geom_point(aes(color = species))
```

Facet Grids for Env. Variables
```{r}
#For surface/depth variables USING DAILY MEAN VARIABLES
# See above for means_08 derivation
track08Long <- means_08 %>%
  pivot_longer(cols = sst_mean:ssh_mean,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("sst_mean", "dist_shore", "chlorophyll_mean", "ssh_mean")) %>%
  rename(Date = `as.Date(UTC)`)

p <- ggplot(data = track08Long, aes(x = Date, y = value)) +
  geom_line()
 # geom_point(aes(size = BWpresence))   ### How best to represent number of BW detections per day?

p + facet_grid(parameter ~ ., scales = "free_y")
  

# For MLD/Thermocline variables 
track08Long2 <- tracks_SS_08 %>%
  pivot_longer(cols = mldDepth:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("mldDepth", "mldTemp", "ttDepth", "ttTemp", "temp400", "sal400")) %>%
    rename(Date = UTC) %>%
    subset(species!="?BW")

q <- ggplot(data = track08Long2, aes(x = Date, y = value)) +
  geom_line() + geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)
q + facet_grid(parameter ~ ., scales = "free_y")

# For temp400 and salinity400 variables
env.labs <- c(`sal400` = "Salinity at 400m", 
              `temp400` = "Temperature at 400m")

track08Long3 <- tracks_SS_08 %>%
  pivot_longer(cols = temp400:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("temp400", "sal400")) %>%
  rename(`Date (2018)` = UTC)

q <- ggplot(data = track08Long3, aes(x = `Date (2018)`, y = value)) +
  geom_line() + 
  geom_point(aes(color = species)) + 
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43", "BW" = "BW"))
q + facet_grid(parameter ~ ., scales = "free_y", labeller = as_labeller(env.labs))
```


Co-occurrence plots of drift 8 and vessels 
```{r}
#### 09/04/18 co-occurrence of vessel and drift within 10 km
track08_09.04 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-04 00:00:00" & UTC <= "2018-09-05 00:00:00")

ggplot(data = track08_09.04, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-04 14:13:00"), color = "yellow", linewidth = 2) +
  geom_text(aes(as.POSIXct("2018-09-04 14:13:00"), 88, label = "Enter vessel", hjust = 1.0)) +
  geom_vline(xintercept = as.POSIXct("2018-09-04 15:17:00"), color = "yellow", linewidth = 2) +
  geom_text(aes(as.POSIXct("2018-09-04 15:13:00"), 87, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.04, aes(color = species, size = 2)) +
  scale_color_discrete(na.translate=FALSE) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-04-18\n(Within 7 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/05/18 co-occurrence of vessel and drift within 10 km.
track08_09.05 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-04 21:00:00" & UTC <= "2018-09-06 00:00:00")

ggplot(data = track08_09.05, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-05 01:33:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-05 01:33:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-05 02:08:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-05 02:08:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.05, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-05-18\n(Within 5 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/10/18 co-occurrence of vessel and drift within 10 km.
track08_09.10 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-10 00:00:00" & UTC <= "2018-09-11 00:00:00")

ggplot(data = track08_09.10, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-10 12:58:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-10 12:58:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-10 14:01:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-10 14:01:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() +
  geom_point(data = track08_09.10, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-10-18\n(Within 2 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))


#### 09/22/18 co-occurrence of vessel and drift within 10 km
track08_09.22 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-22 00:00:00" & UTC <= "2018-09-23 00:00:00")

ggplot(data = track08_09.22, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-22 19:13:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-22 19:13:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-22 19:34:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-22 19:34:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.22, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-22-18\n(Within 9 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/23/18 co-occurrence of vessel and drift within 10 km. NO whale detections in this time period.
track08_09.23 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-23 00:00:00" & UTC <= "2018-09-24 00:00:00")

ggplot(data = track08_09.23, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-23 03:55:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-23 03:55:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-23 04:23:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-23 04:23:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-23-18\n(Within 6 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```

BW Occurrences
```{r}
# Filter Drift 8 by BW presence and absence
BW1 <- tracks_SS_08 %>%
  filter(BWpresence == 1)
BW0 <- tracks_SS_08 %>%
  filter(BWpresence == 0)

ggplot(data = tracks_SS_08, mapping = aes(TOL_125)) + geom_histogram(binwidth = 0.1, color = "black")

ggplot() + 
  geom_histogram(data = BW0, aes(TOL_5000), binwidth = 0.5, fill = "black", color = "white") +
  geom_histogram(data = BW1, aes(TOL_5000), binwidth = 0.5, fill = "yellow", color = "black")

# Percent of time BWs are detected
print(paste(nrow(BW1) / nrow(tracks_SS_08) * 100,"%"))

# Most abundant BW species when whale is detected (remove NA values)
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot() + geom_bar(aes(species))

# Sound levels BW are exposed to by species
ZC <- tracks_SS_08 %>%
  filter(species == "ZC")

BW43 <- tracks_SS_08 %>%
  filter(species == "BW43")

print(max(ZC$TOL_125))
print(max(BW43$TOL_125))
  
ggplot() + geom_histogram(data = ZC, mapping = aes(TOL_125), binwidth = 0.2, fill = "brown", color = "white") +
  geom_histogram(data = BW43, mapping = aes(TOL_125), binwidth = 0.2, fill = "yellow", color = "white") +
  theme_classic()
```


Density Plots - Species at TOL sound levels
```{r}
# Broadband
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(`BB_20.24000`, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("Broadband") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 63
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_63, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("63 Hz") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 125
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_125, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("125 Hz") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 2000
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_2000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("2000 Hz") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 5000
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_5000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("5000 Hz") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
  

# TOL 20,000
tracks_SS_08 %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_20000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("20,000 Hz") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```


Histograms with BW presence/absence and environmental variables
```{r}
# SST
ggplot(data = tracks_SS_08, aes(sst_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.1, color = "black")


# Depth
ggplot(data = tracks_SS_08, aes(depth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 10, color = "black")

# Bottom slope
ggplot(data = tracks_SS_08, aes(slope, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.005, color = "black")

# SSH
ggplot(data = tracks_SS_08, aes(ssh_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.005, color = "black")

# Chlorophyll
ggplot(data = tracks_SS_08, aes(chlorophyll_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.005, color = "black")

# Mixed layer depth Depth
ggplot(data = tracks_SS_08, aes(mldDepth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.25, color = "black")

# Mixed layer depth Temperature
ggplot(data = tracks_SS_08, aes(mldTemp, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.1, color = "black")

# Thermocline Depth
ggplot(data = tracks_SS_08, aes(ttDepth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.25, color = "black")

#Thermocline temperature
ggplot(data = tracks_SS_08, aes(ttTemp, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.05, color = "black")

# Temperature at 400m
ggplot(data = tracks_SS_08, aes(temp400, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.01, color = "black")

# Salinity at 400 m
ggplot(data = tracks_SS_08, aes(sal400, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.001, color = "black")
```


### Plot maps for Powerpoint images

Set Parameters
```{r}
theme_set(theme_bw())
tmap_mode("plot")
```

Create sf objects and basemaps for maps (not needed for environmental variables)
```{r}
whales_8_10sf <- BWsf %>%                            
dplyr::filter(station == "8" | station == "10")

trackssf <- st_as_sf(tracks, coords = c("Longitude", "Latitude"), crs=4326)
trk_TOL_08 <- st_as_sf(tracks_SS_08, coords = c("Longitude", "Latitude"), crs=4326)
trk_TOL_10 <- st_as_sf(tracks_SS_10, coords = c("Longitude", "Latitude"), crs=4326)
trackBase <- get_tiles(whales_8_10sf, provider = "Esri.WorldShadedRelief")
allTrackbase <- get_tiles(trackssf, provider = "Stamen.TonerLite", zoom = 5)
```

Map of whole study area
```{r}
# Establish bounding box
bbox <- st_bbox(c(xmin = -110, 
            xmax = -128, 
            ymax = 44, 
            ymin = 30), crs = st_crs(4326))

#Establish basemap
allTrackbase <- get_tiles(bbox, provider = "Esri.WorldGrayCanvas", zoom = 5)

# Establish inset map
us_region <- st_bbox(c(xmin = -90,
            xmax = -120, 
            ymax = 48, 
            ymin = 25), crs = st_crs(4326))
usa <- get_tiles(us_region, provider = "Esri.WorldGrayCanvas", zoom = 4)

sg <- bb_poly(bb(tracks_sf))
inset <- tm_shape(usa) + tm_rgb() + tm_shape(sg) + tm_borders(col = "red")


#Map all tracks
main <- tm_shape(allTrackbase) + tm_rgb() +
  tm_shape(trackssf) +
  tm_grid(alpha = 0.6, col = "grey") +
  tm_dots(col = "darkblue", size = 0.001, legend.show = TRUE) +
  tm_scale_bar(width = 0.3, text.size = 3, position = c(0.2, 0.03)) +
  tm_compass(type = "arrow", position = c(0.05, 0.05), color.light = "white") +
  tm_add_legend('symbol',
                type = "line",
                col = "darkblue",
                labels = "Drifting buoy tracks",
                size = 1,
                lwd = 2)

vp <- viewport(x=0.66, y=0.8, width = 0.26, height=0.4)
main
print(inset,vp=vp)


# Map all tracks - ggplot
basemap2 <- as.data.frame(allTrackbase, xy = TRUE)
#ggplot() +
#  geom_tile(data = basemap, aes(x=x, y=y, fill = "basemap")) +
#  geom_sf(data = trackssf, mapping = aes(), color = "red")


# Map tracks 08 and 10 only
tm_shape(trackBase) + tm_rgb() + 
  tm_shape(trk_TOL_08) + tm_dots(col = "red", 
                                 legend.show = TRUE) +
  tm_shape(trk_TOL_10) + tm_dots(col = "green")

# Bounding box of drift tracks on map
lon2 <- -129.04666
lon1 <- -115.78247
lat1 <- 28.21790
lat2 <- 45.09226

basemap3 <- ne_countries(scale = "medium", type = "map_units", returnclass = "sf")

# Drift tracks
ggplot(data = basemap3) +
  geom_sf(fill = "antiquewhite") +
  coord_sf(xlim = c(lon2 - 1, lon1 + 1), ylim = c(lat1 - 1, lat2 + 1), expand = FALSE) +
  theme(panel.grid.major = element_blank()) +
  geom_path(data = tracks_sf, mapping = aes(x=long,y=lat, group = factor(station)), color = "deeppink") +
  theme(panel.background = element_rect(fill = "aliceblue"), 
        axis.text = element_blank(), axis.ticks = element_blank(), 
        axis.title = element_blank())
```

Map of soundscapes
```{r}
# CCES_08 + CCES_10 Broadband
tm_shape(trackBase) + tm_rgb() + 
  tm_shape(trk_TOL_08) + 
  tm_symbols(col = "BB_20-24000", 
             border.lwd = NA, 
             size = 0.4, 
             sizes.legend = 0.7, 
             n = 10) +
  tm_shape(trk_TOL_10) + 
  tm_symbols(col = "BB_20-24000",
             border.lwd = NA, 
             size = 0.4,
             n = 10) +
  tm_layout(legend.width = 0.5, 
            legend.position = c("right","top"),
            legend.bg.color = "lightblue")

#CCES_08 Third Octave Level
tm_shape(trackBase) + tm_rgb() + 
  tm_shape(trk_TOL_08) + 
  tm_symbols(col = "TOL_63", 
             border.lwd = NA, 
             size = 0.5, 
             n = 10) + 
  tm_layout(legend.width = 0.5, 
            legend.position = c("right","top")) + 
  tm_legend()

ggplot() + 
  geom_sf(data = trk_TOL_08, aes(color = TOL_125, size = TOL_125), show.legend = FALSE) +
  geom_sf(data = trk_TOL_10, aes(color = TOL_125, size = TOL_125)) +
  scale_x_continuous(limits = c(-130,-122)) + 
  scale_y_continuous(limits = c(35,39)) +
  scale_color_gradient(low = "navy", high = "yellow")+
  scale_size(range = c(1,12)) +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(panel.border = element_rect(fill = NA),
        axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.position = "none")
```

Map of whale detections
```{r}
# Whale detections
ggplot() +
  geom_point(data = whales8, mapping = aes(x=long, y=lat), shape = 21, color = "black", fill = "green4", size = 4) +
  geom_point(data = whales10, mapping = aes(x=long, y=lat), shape = 21, color = "black", fill = "green4", size = 4) +
  scale_x_continuous(limits = c(-130,-122)) + 
  scale_y_continuous(limits = c(35,39)) +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(panel.border = element_rect(fill = NA),
        axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank()
        )
#ggsave("BWdetect.png")


```

Map of bathymetry
```{r}
# Bathymetry
bathym <- ggplot() +
    geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`)) +
  annotation_scale(location = "bl", width_hint = 0.4) +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))


# Alternative Bathymetry (code from Ocean Tracking Network #https://www.youtube.com/watch?v=xT2F-Y9bKLk)
bgo <- getNOAA.bathy(lon1 = -122, lon2 = -130,
                     lat1 = 35, lat2= 39, resolution = 1)  # plot bounding box around drift 8 and 10
autoplot(bgo, geom = c("raster", "contour"), coast = TRUE, show.legend = FALSE) + 
  scale_fill_etopo() + #creates ggplot object
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank())

# Soundscape + bathymetry
whales08_sf <- BWsf %>%                            
  dplyr::filter(station == "8")

ggplot() +
  geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`), show.legend = FALSE) +
  #geom_contour(data = bathy_df, mapping = aes(x=x, y=y, z=gebco_bathy, linewidth = 0.1), color = "blue", linewidth = 0.01,) +
  geom_sf(data = trk_TOL_08, aes(color = TOL_125, size = TOL_125), show.legend = FALSE) +
  geom_sf(data = whales08_sf, aes(), color = "black") +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  scale_color_gradient(low = "beige", high = "hotpink") +
  scale_fill_etopo() +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))
#ggsave("soundscape.png")
```

Map of AIS
```{r}
# Plot + crop to drift area
#basemap <- ne_countries(scale = "medium", returnclass = "sf")
#ggplot() + 
#  geom_sf(aes(), basemap) +
#  geom_path(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName), #show.legend = F) + 
  #geom_point(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName)) +
#  scale_x_continuous(limits = c(min(drift$long-0.7), max(drift$long + 0.7))) + 
#  scale_y_continuous(limits = c(min(drift$lat-0.7), max(drift$lat + 0.7)))


# AIS data
ggplot() + 
  geom_path(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName, linewidth = 1), show.legend = F) +
  scale_x_continuous(limits = c(-131,-121)) + 
  scale_y_continuous(limits = c(34,40)) +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))
#ggsave("AIS.png")
```


Map of Sea Surface Temp with rerddap, Drift 8 only
```{r}
# Multi-scale Ultra-high Resolution (MUR) SST Analysis fv04.1, Global, 0.01, 2002-present, Daily
SSTInfo <- info('jplMURSST41') 
murSST <- griddap(SSTInfo, latitude = c(35, 39), longitude = c(-122, -130), 
                  time = c("2018-08-16", "2018-10-01"), 
                  fields = 'analysed_sst') # drift 8 dates only
SST <- murSST$data

# Raster of SST
ggplot() + 
  geom_tile(data = SST, aes(x = longitude, y = latitude, fill = analysed_sst)) +
  scale_fill_gradient(low = "darkblue", high = "yellow") +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA),
        legend.position = "none")
```

Plot distance to continental slope
```{r}
ggplot() +
  geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`)) +
  geom_sf(data = tracks_SS_08, 
          mapping = aes(col = dist_slope)) +
  geom_sf(data = cont_slope) + scale_fill_continuous(high = "lightgreen", low = "blue")
  

# PLOT distance by TOL with whales
ggplot(data = tracks_SS_08, aes(x = dist_slope, y = `TOL_125`)) + 
  geom_point() + 
  geom_smooth(color = "green") +
  theme_classic()
```

Another map - need to decide if important to keep
```{r}
# Plot
oceanBase <- get_tiles(tracks_SS_08, provider="Esri.NatGeoWorldMap", crop = TRUE)
tm_shape(oceanBase) + tm_rgb() +
  tm_shape(tracks_SS_08) +  tm_symbols(col="species", size = 1) +
  tm_layout(legend.width = 0.5, 
            legend.position = c("right","top"))


#Raster base map
oceanBase <- get_tiles(tracks_SS_10, provider="Esri.NatGeoWorldMap")
tm_shape(bathy) + tm_raster() +
  tm_shape(tracks_SS_10) + 
  tm_symbols(style = "jenks") +
  tm_layout(legend.width = 0.5)
```

```{r}
# Plots for coastline and continental slope. Do I keep?
sf08 <- st_as_sf(tracks_SS_08, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
sf10 <- st_as_sf(tracks_SS_10, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
trkraster08 <- rasterize(vect(sf08), agg)
trkraster10 <- rasterize(vect(sf10), agg)

bathy_df <- as.data.frame(bathy, xy = TRUE)

# Map the coastline and cont. slope
cont <- st_as_sf(as.contour(bathy, ))
coast <- cont %>% filter(level == 0)
cont_slope <- cont %>% filter(level == -2000) #Is 2000m the correct depth for continental shelf?
cont_slope_rast <- rasterize(cont_slope, agg, field = "level")
plot(agg)
plot(cont_slope_rast, col = "red")
cont_slope_rast <- rasterize(cont_slope, agg)
plot(cont_slope_rast, col = "red")
  
ggplot() + 
  geom_sf(data = cont, col="black") + 
  geom_sf(data = coast, col = "red") +
  geom_sf(data = cont_slope, col = "purple") +
  #geom_sf(data = whales_8_10sf, mapping = aes()) +
  scale_color_gradient(low="green", high="red")
```

