---
title: " extracting environmenal and oceanographic variables"
output: html_document
date: "2022-11-06"
---

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
#library(raster)
library(terra)
library(PAMpal)
library(PAMmisc)
#library(marmap)
library(rerddap)
```

### Get Environmental Variables

For each buoy, the value of each environmental variable will be added to each track point based on Lat, Long, and UTC.
Data only need to be downloaded once. After that, can refer to the file in the external hard drive ("D:").

Environmental variables: Sea surface temp, Wind stress curl, Distance to continental slope, Depth, bathymetric slope,
distance to shore, chlorophyll, sea surface height anomalies, + Hycom variables.

Sea Surface Temperature from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST07", var = c('analysed_sst'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST08", var = c('analysed_sst'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST10", var = c('analysed_sst'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST12", var = c('analysed_sst'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST13", var = c('analysed_sst'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST14", var = c('analysed_sst'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST16", var = c('analysed_sst'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST18", var = c('analysed_sst'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST19", var = c('analysed_sst'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST20", var = c('analysed_sst'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST21", var = c('analysed_sst'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST22", var = c('analysed_sst'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST23", var = c('analysed_sst'))
```

Once downloaded, matches SST from file
```{r}
SSTlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="analysedSST")

for (ss in SSTlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ss, 33, 34))), nc = ss) %>%
  rename(., sst_mean = analysed_sst_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)   # rename new column to "sst_mean" and remove unnecessary columns

  assign(paste0("tracks_SS_", substr(ss, 33, 34)), data)
}
```
### Wind Stress Curl from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress07.nc", var = c('curl'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress08.nc", var = c('curl'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress10.nc", var = c('curl'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress12.nc", var = c('curl'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress13.nc", var = c('curl'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress14.nc", var = c('curl'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress16.nc", var = c('curl'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress18.nc", var = c('curl'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress19.nc", var = c('curl'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress20.nc", var = c('curl'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress21.nc", var = c('curl'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress22.nc", var = c('curl'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress23.nc", var = c('curl'))

# Pulls from downloaded file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data-raw/erdQMstress1day_LonPM180.nc')
#tracks_SS_08

#windcurl <- erddapToEdinfo('erdQMstress1day', baseurl = 'https://coastwatch.pfeg.noaa.gov/erddap/')

#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc=windcurl, fileName='windcurl.nc')

```
Once downloaded, matches wind stress curl from file
```{r}
windlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="windstress")

for (w in windlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(w, 32, 33))), nc = w) %>%
     dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean, -matchDepth_mean)   # remove unnecessary columns
  
  assign(paste0("tracks_SS_", substr(w, 32, 33)), data)
}
```

### Distance to continental slope (uses terra package)
```{r}
bathy <- rast("D:/CCES_gebco_bathy.tif") # Bathymetry for all of CCE from https://download.gebco.net/
agg <- terra::aggregate(bathy, 5)  # Increase cell size by factor of 5 to be visible

cont <- st_as_sf(as.contour(bathy, )) # Create contour lines from bathymetry 
cont_slope <- cont %>% filter(level == -2000) # Establish continental shelf. Is 2000m the correct depth for continental shelf?

tracklist <- grep(pattern = "tracks_SS_", names(.GlobalEnv), value = T)

for (t in tracklist) {
  sf <- st_as_sf(get(t), coords = c("Longitude", "Latitude"), crs=4326, remove=F)
  trk <- terra::rasterize(vect(sf), agg)
  slop <- terra::distance(trk, vect(cont_slope))
  ext <- terra::extract(slop, vect(sf))
  
  dbind <- cbind(sf, ext) %>%
  dplyr::select(-ID) %>%
  rename("dist2slope" = last) %>%
  st_set_geometry(NULL) # remove geometry to prevent buoy dataframe from becoming sf object for future 
  
  assign(paste0("tracks_SS_", substr(t, 11, 12)), dbind)
}
```

Depth from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth07.nc", var = c('z'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth08.nc", var = c('z'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth10.nc", var = c('z'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth12.nc", var = c('z'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth13.nc", var = c('z'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth14.nc", var = c('z'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth16.nc", var = c('z'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth18.nc", var = c('z'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth19.nc", var = c('z'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth20.nc", var = c('z'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth21.nc", var = c('z'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth22.nc", var = c('z'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth23.nc", var = c('z'))
```

Once downloaded, matches depth from file
```{r}
depthlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="depth")

for (dd in depthlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(dd, 27, 28))), nc = dd) %>%
  rename(., depth = z_mean) %>%        # rename new column to "depth"
  mutate(depth = depth*-1) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(dd, 27, 28)), data)
}
```

#### Bathymetric slope (skipping loop for now)
```{r}
bathy_slope <- terra::terrain(bathy, v = "slope")

for (t in tracklist) {
  slope <- terra::extract(bathy_slope, get(t)[,4:3]) %>%  # Reads latitude and longitude of buoy dataframe
  dplyr::select(-ID) %>%
  rename("bathy_slope" = slope)
  
  sbind <- cbind(get(t), slope)
  
  assign(paste0("tracks_SS_", substr(t, 11, 12)), sbind)
}
```

Distance to Shore from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore07.nc", var = c('dist'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore08.nc", var = c('dist'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore10.nc", var = c('dist'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore12.nc", var = c('dist'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore13.nc", var = c('dist'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore14.nc", var = c('dist'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore16.nc", var = c('dist'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore18.nc", var = c('dist'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore19.nc", var = c('dist'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore20.nc", var = c('dist'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore21.nc", var = c('dist'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore22.nc", var = c('dist'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore23.nc", var = c('dist'))
```

Once downloaded, matches Distance to Shore from file
```{r}
distlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="dist2shore")

for (d2 in distlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(d2, 32, 33))), nc = d2) %>%
  rename(., dist2shore = dist_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(d2, 32, 33)), data)
}
```

### Chlorophyll from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll07.nc", var = c('chlorophyll'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll08.nc", var = c('chlorophyll'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll10.nc", var = c('chlorophyll'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll12.nc", var = c('chlorophyll'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll13.nc", var = c('chlorophyll'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll14.nc", var = c('chlorophyll'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll16.nc", var = c('chlorophyll'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll18.nc", var = c('chlorophyll'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll19.nc", var = c('chlorophyll'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll20.nc", var = c('chlorophyll'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll21.nc", var = c('chlorophyll'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll22.nc", var = c('chlorophyll'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll23.nc", var = c('chlorophyll'))
```

Once downloaded, matches chlorophyll from file
```{r}
chlalist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="chlorophyll")

for (ch in chlalist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ch, 33, 34))), nc = ch) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(ch, 33, 34)), data)
}
```

Sea Surface Height Anomalies from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh07.nc", var = c('sla'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh08.nc", var = c('sla'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh10.nc", var = c('sla'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh12.nc", var = c('sla'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh13.nc", var = c('sla'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh14.nc", var = c('sla'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh16.nc", var = c('sla'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh18.nc", var = c('sla'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh19.nc", var = c('sla'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh20.nc", var = c('sla'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh21.nc", var = c('sla'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh22.nc", var = c('sla'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh23.nc", var = c('sla'))
```

Once downloaded, matches sea surface height anomalies from file
```{r}
sshlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="ssh")

for (sh in sshlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(sh, 25, 26))), nc = sh) %>%
  rename(., ssh_mean = sla_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(sh, 25, 26)), data)
}
```


#### HyCOM Data - MLDepth, MLTemp, TTemp, TDepth, Salinity

Create function to estimate thermocline variables using the temperature at depth data
```{r}
calcThermoVars <- function(depth, temp, mldMode='SST8', thermMode='variso', plot=FALSE) {
    # depthInterp <- approxfun(x=temp, y=depth)
    switch(match.arg(mldMode),
           'SST8' = {
               mldTemp <- temp[1] - 0.8
               # first few temps are likely to have repeat values that trigger
               # warnings for approxfun, so cut off to only values after mldTemp
               useMin <- min(which(temp <= mldTemp)) - 1
               useIx <- useMin:length(temp)
               depthInterp <- approxfun(x=temp[useIx], y=depth[useIx])
               mld <- depthInterp(mldTemp)
           }
    )
    switch(match.arg(thermMode),
           'variso' = {
               t400 <- approx(x=depth, y=temp, xout=400)$y
               # therm end is half way to t400 temp
               tEnd <- mldTemp + (t400 - mldTemp)/2
               # therm temp is midpt from mld to end
               tt <- (mldTemp + tEnd)/2
               # tt <- mldTemp - .25 * (mldTemp - t400)
               ttDepth <- depthInterp(tt)
               tEndDepth <- depthInterp(tEnd)
           }
    )
    if(plot) {
        to300 <- depth <= 300
        plot(x=temp[to300], y=-depth[to300],
             main = paste0('MixLayer: ', round(mld,0), 'm ', round(mldTemp, 1), 'C',
                           '\nTherm: ', round(ttDepth, 0), 'm ', round(tt, 1), 'C'),
             xlab='Temp (C)', ylab='Depth (m)')
        
        lines(x=temp[to300], y=-depth[to300])
        lines(x=c(mldTemp, tEnd), y=c(-mld, -tEndDepth), col='darkgray', lwd=4)
        points(x=c(mldTemp, tt), y=c(-mld, -ttDepth), col='blue', cex=1.5, pch=15)
    }
    list(mldDepth = mld, mldTemp = mldTemp,
         ttDepth = ttDepth, ttTemp = tt)
}
```


```{r}
# Create loop for each buoy to download HYCOM data

## This only downloads 11 of 13 successfully - FIX
for (t in tracklist) {
  Hdata <- matchEnvData(as.data.frame(get(paste0("tracks_SS_", substr(t, 11, 12)))), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)
  
  thermData <- bind_rows(lapply(Hdata, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))
  bindr <- cbind(get(paste0("tracks_SS_", substr(t, 11, 12))), thermData)
  assign(paste0("tracks_SS_", substr(t, 11, 12)), bindr)
}
```

```{r}
## HYCOM function above stops at buoys 07 and 08, need to manually run it here. FIX!!
test08 <- matchEnvData(as.data.frame(tracks_SS_08), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

thermData08 <- bind_rows(lapply(test08, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

tracks_SS_08 <- cbind(tracks_SS_08, thermData08)
```


Save final buoy df for analysis use next.
```{r}
saveRDS(tracks_SS_10, 'data/fulltrack10.rda')
saveRDS(tracks_SS_12, 'data/fulltrack12.rda')
saveRDS(tracks_SS_13, 'data/fulltrack13.rda')
saveRDS(tracks_SS_14, 'data/fulltrack14.rda')
saveRDS(tracks_SS_16, 'data/fulltrack16.rda')
saveRDS(tracks_SS_18, 'data/fulltrack18.rda')
saveRDS(tracks_SS_19, 'data/fulltrack19.rda')
saveRDS(tracks_SS_20, 'data/fulltrack20.rda')
saveRDS(tracks_SS_21, 'data/fulltrack21.rda')
saveRDS(tracks_SS_22, 'data/fulltrack22.rda')
saveRDS(tracks_SS_23, 'data/fulltrack23.rda')
saveRDS(tracks_SS_07, 'data/fulltrack07.rda')
saveRDS(tracks_SS_08, 'data/fulltrack08.rda')

# also saves to external hard drive
saveRDS(tracks_SS_10, 'D:/Buoy_dfs/fulltrack10.rda')
saveRDS(tracks_SS_12, 'D:/Buoy_dfs/fulltrack12.rda')
saveRDS(tracks_SS_13, 'D:/Buoy_dfs/fulltrack13.rda')
saveRDS(tracks_SS_14, 'D:/Buoy_dfs/fulltrack14.rda')
saveRDS(tracks_SS_16, 'D:/Buoy_dfs/fulltrack16.rda')
saveRDS(tracks_SS_18, 'D:/Buoy_dfs/fulltrack18.rda')
saveRDS(tracks_SS_19, 'D:/Buoy_dfs/fulltrack19.rda')
saveRDS(tracks_SS_20, 'D:/Buoy_dfs/fulltrack20.rda')
saveRDS(tracks_SS_21, 'D:/Buoy_dfs/fulltrack21.rda')
saveRDS(tracks_SS_22, 'D:/Buoy_dfs/fulltrack22.rda')
saveRDS(tracks_SS_23, 'D:/Buoy_dfs/fulltrack23.rda')
saveRDS(tracks_SS_07, 'D:/Buoy_dfs/fulltrack07.rda')
saveRDS(tracks_SS_08, 'D:/Buoy_dfs/fulltrack08.rda')
```
