---
title: "04_analysis"
author: "Marina Bozinovic"
date: "2023-05-11"
output: html_document
---
# Exploratory Analysis and Modeling for all 13 buoys

Required Packages
```{r}
library(tidyverse)
library(mgcv)
```

Read in RDS files of each buoy + all environ variables + AIS (pending)
```{r}
ftlist <- dir("data/", recursive=TRUE, full.names=TRUE, pattern="fulltrack")

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("fulltrack", substr(ft, 15, 16)), df)
}

```

Bind ALL DRIFTS into one dataframe
```{r}
allDrifts <- rbind(fulltrack07, fulltrack08, fulltrack10, fulltrack12, fulltrack13, fulltrack14, 
                   fulltrack16, fulltrack18, fulltrack19, fulltrack20, fulltrack21, fulltrack22, fulltrack23)
save(allDrifts, file = "allDrifts.rda")
```


### Third octave levels histograms

```{r all-drifts-all-freq-histogram}
# create list of fulltrack dfs from global environment to loop through
dlist <- grep(pattern = "fulltrack", names(.GlobalEnv), value = T)

# all Drifts - all TOL bands, facet wrap
for (ft in dlist) {
pivot1 <- get(ft) %>%
  pivot_longer(cols = starts_with("TOL") | starts_with("BB"), names_to = "SL", values_to = "Hz")    # Pivot longer for histogram facet grid

print(ggplot(data = pivot1, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 3, color = "black") +
  theme_classic() +
  ggtitle(paste0("Distribution of third octave level intensities: Drift ", substr(ft,10,11))) +
  labs(x = "Sound Intensity (dB)") +
  guides(fill = guide_legend(title = "Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.7,0.8)) +
  (facet_grid(~factor(SL, levels = c('BB_20.24000', 'TOL_63', 'TOL_125', 'TOL_2000', 'TOL_5000', 'TOL_20000')))))
}

# Single plot for ALL DRIFTS
pivot3 <- allDrifts %>%
  pivot_longer(cols = starts_with("TOL") | starts_with("BB"), names_to = "SL", values_to = "Hz")    # Pivot longer for histogram facet grid

#SL$size_f <- factor(SL$ , levels = c('BB_20.2400', 'TOL_63', 'TOL_125', 'TOL_2000', 'TOL_5000', 'TOL_20000'))))

ggplot(data = pivot3, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 3, color = "black") +
  theme_classic() +
  ggtitle("Distribution of third octave level intensities: All Drifts Combined") +
  labs(x = "Sound Intensity (dB)") +
  guides(fill = guide_legend(title = "Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.7,0.8)) +
  facet_grid(~factor(SL, levels = c('BB_20.24000', 'TOL_63', 'TOL_125', 'TOL_2000', 'TOL_5000', 'TOL_20000')))

```

## ignore??
```{r drift-8-histogram}
#ggplot(data = pivot3, aes(Hz, fill = factor(BWpresence))) +
#  geom_histogram(binwidth = 1, color = "black") +
#  theme_classic() +
#  ggtitle("Distribution of Third-Octave Level (TOL) Intensities: Buoy 8") +
#  scale_x_continuous(name = "Sound Intensity (dB)") +
#  scale_fill_manual(name = "Beaked Whale Presence", 
#                    labels = c("0" = "Absent", "1" = "Present"),
#                    values = c("0" = "bisque1",
#                               "1" = "brown4")) +
#  theme(legend.position = c(0.6,0.7)) +
#  facet_wrap(~TOL, labeller = as_labeller(TOL.labs))
```


```{r all-drifts-two-freq-histogram}
# All Drifts - TOL bands 125 and 2000 only

TOL.labs <- c(`TOL_125` = "TOL at 125 Hz", 
              `TOL_2000` = "TOL at 2000 Hz") #creates label names for plots below

for (ft in dlist) {
pivot2 <- get(ft) %>%
  dplyr::select(-TOL_63, -TOL_20000, -TOL_5000) %>%
  pivot_longer(cols = starts_with("TOL"), names_to = "TOL", values_to = "Hz")    # Pivot longer for histogram facet grid

print(ggplot(data = pivot2, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 1, color = "black") +
  theme_classic() +
  ggtitle(paste0("Distribution of Third-Octave Level (TOL) Intensities: Drift ", substr(ft,10,11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_manual(name = "Whale Presence", 
                    labels = c("0" = "Absent", "1" = "Present"),
                    values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.6,0.7)) +
  facet_wrap(~TOL, labeller = as_labeller(TOL.labs)))
}


# Single plot for ALL DRIFTS combined
pivot4 <- allDrifts %>%
  dplyr::select(-TOL_63, -TOL_20000, -TOL_5000) %>%
  pivot_longer(cols = starts_with("TOL"), names_to = "TOL", values_to = "Hz")    # Pivot longer for histogram facet grid

ggplot(data = pivot4, aes(Hz, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 1, color = "black") +
  theme_classic() +
  ggtitle("Distribution of Third-Octave Level (TOL) Intensities: All Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_manual(name = "Whale Presence", 
                    labels = c("0" = "Absent", "1" = "Present"),
                    values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.6,0.7)) +
  facet_wrap(~TOL, labeller = as_labeller(TOL.labs))
```

Timeline of drifts in ocean
```{r}
ggplot(data = allDrifts, aes(x = UTC, y = station*(-1))) + geom_point(aes(color = factor(station)))

#Note the break in drift 20 - I think it wasn't transmitting for several days (11/15-11/19)
```

Avg sound levels by band (scatterplot)
```{r}
avgdB <- TO_23 %>%
  summarize(TOL_25 = mean(TOL_25),
            TOL_31.5 = mean(TOL_31.5),
            TOL_40 = mean(TOL_40),
            TOL_50 = mean(TOL_50),
            TOL_63 = mean(TOL_63),
            TOL_80 = mean(TOL_80),
            TOL_100 = mean(TOL_100),
            TOL_125 = mean(TOL_125),
            TOL_160 = mean(TOL_160),
            TOL_200 = mean(TOL_200),
            TOL_250 = mean(TOL_250),
            TOL_315 = mean(TOL_315),
            TOL_400 = mean(TOL_400),
            TOL_500 = mean(TOL_500),
            TOL_630 = mean(TOL_630),
            TOL_800 = mean(TOL_800),
            TOL_1000 = mean(TOL_1000),
            TOL_1250 = mean(TOL_1250),
            TOL_1600 = mean(TOL_1600),
            TOL_2000 = mean(TOL_2000),
            TOL_2500 = mean(TOL_2500),
            TOL_3150 = mean(TOL_3150),
            TOL_4000 = mean(TOL_4000),
            TOL_5000 = mean(TOL_5000),
            TOL_6300 = mean(TOL_6300),
            TOL_8000 = mean(TOL_8000),
            TOL_10000 = mean(TOL_10000),
            TOL_12500 = mean(TOL_12500),
            TOL_16000 = mean(TOL_16000),
            TOL_20000 = mean(TOL_20000)) %>%
  pivot_longer(cols = TOL_25:TOL_20000,
               names_to = "frequency",
               values_to="dB")


ggplot(avgdB, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Looking at TOl2000 sound levels for each buoy and where Whale Detections happen
```{r fig.width=10}
ggplot(fulltrack23, aes(x = UTC, y = TOL_2000)) + geom_line() + 
  geom_smooth() + 
  geom_point(aes(color = species, size = 2)) +
  geom_point(color = shipin10km) +
  scale_color_discrete(na.translate=FALSE)
```



Box plots
```{r}
TO_longer <- pivot_longer(TO_10, cols = TOL_25:TOL_20000,
               names_to = "frequency",
               values_to="dB")
ggplot(TO_longer, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Violin plot
ggplot(TO_longer, aes(x = factor(frequency, levels = unique(frequency)), y = dB)) + 
  geom_violin() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
ggplot(allDrifts, aes(factor(BWpresence), TOL_2000)) + geom_boxplot()
```




Scatterplots

```{r}
# SST vs TOL 2000
ggplot(data = allDrifts, aes(x = sst_mean, y = `TOL_2000`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# SST over time (strange plot)
ggplot(allDrifts, aes(x = UTC, y = sst_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")


# Depth vs TOL 125
ggplot(data = allDrifts, aes(x = depth, y = `TOL_125`)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

#Mean depth over time
#ggplot(means_08, aes(x = `as.Date(UTC)`, y = depth*(-1))) +
#  geom_line()

# Chlorophyll vs TOL 125
ggplot(data = allDrifts, aes(x = chlorophyll_mean, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# CHl over time
ggplot(allDrifts, aes(x = UTC, y = chlorophyll_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")

# Mixed Layer Depth vs TOL125 with species
ggplot(data = allDrifts, aes(x = mldDepth, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# Mixed Layer Depth over time
ggplot(allDrifts, aes(x = UTC, y = mldDepth*(-1))) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

ggplot(data = allDrifts, aes(x = `TOL_125`, y = bathy_slope)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)
  
```



Facet Grids for Env. Variables
```{r}
#Get avg daily environmental variables
means <- allDrifts %>%
  group_by(as.Date(UTC))%>%
  summarize(sst_mean = mean(sst_mean),
            dist_slope = mean(dist2slope),
            depth = mean(depth),
            slope = mean(bathy_slope),
            dist_shore = mean(dist2shore),
            chlorophyll_mean = mean(chlorophyll_mean),
            ssh_mean = mean(ssh_mean),
            mldDepth = mean(mldDepth),
            mldTemp = mean(mldTemp),
            ttDepth = mean(ttDepth),
            ttTemp = mean(ttTemp),
            temp400 = mean(temp400),
            sal400 = mean(sal400),
            curlmean = mean(curl_mean),
            Wh_presence = sum(BWpresence))
```

```{r}
#For surface/depth variables USING DAILY MEAN VARIABLES
trackLong <- means %>%
  pivot_longer(cols = sst_mean:ssh_mean,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("sst_mean", "dist_shore", "chlorophyll_mean", "ssh_mean")) %>%
  rename(Date = `as.Date(UTC)`)

p <- ggplot(data = trackLong, aes(x = Date, y = value)) +
  geom_line()

p + facet_grid(parameter ~ ., scales = "free_y")
  

# For MLD/Thermocline variables 
trackLong2 <- allDrifts %>%
  pivot_longer(cols = mldDepth:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("mldDepth", "mldTemp", "ttDepth", "ttTemp", "temp400", "sal400")) %>%
    rename(Date = UTC) %>%
    subset(species!="?BW")

q <- ggplot(data = trackLong2, aes(x = Date, y = value)) +
  geom_line() + geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)
q + facet_grid(parameter ~ ., scales = "free_y")

# For temp400 and salinity400 variables
env.labs <- c(`sal400` = "Salinity at 400m", 
              `temp400` = "Temperature at 400m")

trackLong3 <- allDrifts %>%
  pivot_longer(cols = temp400:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("temp400", "sal400")) %>%
  rename(`Date (2018)` = UTC)

q <- ggplot(data = trackLong3, aes(x = `Date (2018)`, y = value)) +
  #geom_line() + 
  geom_point(aes(color = species)) + 
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43", "BW" = "BW"))
q + facet_grid(parameter ~ ., scales = "free_y", labeller = as_labeller(env.labs))
```


NEEDS FIXING/LOOP/AIS DATA FOR OTHER DRIFTS
Co-occurrence plots of drift 8 and vessels 
```{r}
#### 09/04/18 co-occurrence of vessel and drift within 10 km
track08_09.04 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-04 00:00:00" & UTC <= "2018-09-05 00:00:00")

ggplot(data = track08_09.04, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-04 14:13:00"), color = "yellow", linewidth = 2) +
  geom_text(aes(as.POSIXct("2018-09-04 14:13:00"), 88, label = "Enter vessel", hjust = 1.0)) +
  geom_vline(xintercept = as.POSIXct("2018-09-04 15:17:00"), color = "yellow", linewidth = 2) +
  geom_text(aes(as.POSIXct("2018-09-04 15:13:00"), 87, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.04, aes(color = species, size = 2)) +
  scale_color_discrete(na.translate=FALSE) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-04-18\n(Within 7 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/05/18 co-occurrence of vessel and drift within 10 km.
track08_09.05 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-04 21:00:00" & UTC <= "2018-09-06 00:00:00")

ggplot(data = track08_09.05, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-05 01:33:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-05 01:33:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-05 02:08:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-05 02:08:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.05, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-05-18\n(Within 5 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/10/18 co-occurrence of vessel and drift within 10 km.
track08_09.10 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-10 00:00:00" & UTC <= "2018-09-11 00:00:00")

ggplot(data = track08_09.10, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-10 12:58:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-10 12:58:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-10 14:01:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-10 14:01:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() +
  geom_point(data = track08_09.10, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-10-18\n(Within 2 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))


#### 09/22/18 co-occurrence of vessel and drift within 10 km
track08_09.22 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-22 00:00:00" & UTC <= "2018-09-23 00:00:00")

ggplot(data = track08_09.22, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-22 19:13:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-22 19:13:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-22 19:34:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-22 19:34:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() + 
  geom_point(data = track08_09.22, aes(color = species, size = 2)) +
  scale_size_continuous(guide = "none") +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-22-18\n(Within 9 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

#### 09/23/18 co-occurrence of vessel and drift within 10 km. NO whale detections in this time period.
track08_09.23 <- tracks_SS_08 %>%
  filter(UTC >= "2018-09-23 00:00:00" & UTC <= "2018-09-24 00:00:00")

ggplot(data = track08_09.23, aes(x = UTC, y = `TOL_125`)) +
  geom_vline(xintercept = as.POSIXct("2018-09-23 03:55:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-23 03:55:00"), 86, label = "Enter vessel", hjust = 1)) +
  geom_vline(xintercept = as.POSIXct("2018-09-23 04:23:00"), color = "yellow", linewidth = 1) +
  geom_text(aes(as.POSIXct("2018-09-23 04:23:00"), 85, label = "Exit vessel", hjust = -0.1)) +
  geom_line() +
  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-23-18\n(Within 6 km)") +
  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```


IS THIS HELPFUL??
Whale Occurrences
```{r}
# Filter Drift 8 by Whale presence and absence
W1 <- tracks_SS_08 %>%
  filter(Wpresence == 1)
W0 <- tracks_SS_08 %>%
  filter(Wpresence == 0)

ggplot(data = tracks_SS_08, mapping = aes(TOL_125)) + geom_histogram(binwidth = 0.1, color = "black")

ggplot() + 
  geom_histogram(data = W0, aes(TOL_5000), binwidth = 0.5, fill = "black", color = "white") +
  geom_histogram(data = W1, aes(TOL_5000), binwidth = 0.5, fill = "yellow", color = "black")

# Percent of time BWs are detected
print(paste(nrow(W1) / nrow(tracks_SS_08) * 100,"%"))

# Most abundant whale species when whale is detected (remove NA values)
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot() + geom_bar(aes(species))

# Sound levels whales are exposed to by species
ZC <- allDrifts %>%
  filter(species == "ZC")

BW43 <- allDrifts %>%
  filter(species == "BW43")

BB <- allDrifts %>%
  filter(species == "BB")

BWC <- allDrifts %>%
  filter(species == "BWC")

BW37V <- allDrifts %>%
  filter(species == "BW37V")

PM <- allDrifts %>%
  filter(species == "PM")

print(max(ZC$TOL_125))
print(max(BW43$TOL_125))
print(max(BB$TOL_125))
print(max(BWC$TOL_125))
print(max(BW37V$TOL_125))
print(max(PM$TOL_125))

  
ggplot() + geom_histogram(data = ZC, mapping = aes(TOL_125), binwidth = 0.2, fill = "brown", color = "white") +
  geom_histogram(data = BW43, mapping = aes(TOL_125), binwidth = 0.2, fill = "yellow", color = "white") +
  theme_classic()
```


Density Plots - Species at TOL sound levels
```{r density-plots}
# Broadband
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(`BB_20.24000`, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("Broadband Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# Broadband SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(`BB_20.24000`, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("Broadband ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
 
# TOL 63
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_63, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 63, Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 63 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_63, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 63 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 125
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_125, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 125, Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 125 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_125, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 125 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 2000
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_2000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 2000, Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 2000 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_2000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 2000 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 5000
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_5000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 5000, Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 5000 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_5000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 5000 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 20,000
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_20000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 20000, Drift ", substr(ft, 10, 11))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 20,000 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_20000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 20,000 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```

ARE THESE HELPFUL??
Histograms with whale presence/absence and environmental variables. Doesnt differentiate by species though
```{r}
# SST
ggplot(data = allDrifts, aes(sst_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.1, color = "black")

# Depth
ggplot(data = allDrifts, aes(depth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 100, color = "black")

# Bottom slope
ggplot(data = allDrifts, aes(bathy_slope, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 1, color = "black")

# SSH
ggplot(data = allDrifts, aes(ssh_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.005, color = "black")

# Chlorophyll
ggplot(data = allDrifts, aes(chlorophyll_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.05, color = "black")

#Wind Curl
ggplot(data = allDrifts, aes(curl_mean, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.0000005, color = "black")

# Mixed layer depth Depth
ggplot(data = allDrifts, aes(mldDepth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.25, color = "black")

# Mixed layer depth Temperature
ggplot(data = allDrifts, aes(mldTemp, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.1, color = "black")

# Thermocline Depth
ggplot(data = allDrifts, aes(ttDepth, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.75, color = "black")

#Thermocline temperature
ggplot(data = allDrifts, aes(ttTemp, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.1, color = "black")

# Temperature at 400m
ggplot(data = allDrifts, aes(temp400, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.03, color = "black")

# Salinity at 400 m
ggplot(data = allDrifts, aes(sal400, fill = factor(BWpresence))) +
  geom_histogram(binwidth = 0.005, color = "black")
```


### GAMs

```{r}
model3 <- gam(BWpresence ~ depth + TOL_125 + dist2shore + mldTemp, 
              data = allDrifts, family = binomial)
#plot(model3)

#try fitting linear model

lm_depth <- lm(BWpresence ~ depth, data = allDrifts)
ggplot(allDrifts, aes(sst_mean, chlorophyll_mean)) +
  geom_point() +
  geom_smooth()
```
Categorical term
```{r}
# ALL variables, GAM
model1 <- gam(BWpresence>0 ~ s(BB_20.24000) + s(TOL_63) + s(TOL_125) + s(TOL_2000)
              + s(TOL_5000) + s(TOL_20000) + s(depth) + s(mldDepth) + s(Latitude)
              + s(Longitude) + s(sst_mean) + s(curl_mean) + s(dist2slope) 
              + s(bathy_slope) + s(dist2shore) + s(chlorophyll_mean) + s(ssh_mean) 
              + s(mldTemp) + s(ttDepth) + s(ttTemp) + s(temp400) + s(sal400),
              data = allDrifts, family = binomial, method = "REML")

# ALL variables, GLM
model1GLM <- glm(BWpresence ~ BB_20.24000 + TOL_63 + TOL_125 + TOL_2000
              + TOL_5000 + TOL_20000 + depth + mldDepth + Latitude
              + Longitude + sst_mean + curl_mean + dist2slope
              + bathy_slope + dist2shore + chlorophyll_mean + ssh_mean 
              + mldTemp + ttDepth + ttTemp + temp400 + sal400,
              data = allDrifts, family = binomial)

# By species? doesnt work, may need to create dummy variables
model2 <- gam(BWpresence ~ s(sst_mean, by = as.factor(species)), 
              data = allDrifts, family = binomial, method = "REML")

# Soundscape metrics only, GAM
model4 <- gam(BWpresence ~ s(BB_20.24000, k = 10) + 
                s(TOL_63, k = 10) + s(TOL_125, k = 10) + 
                s(TOL_2000, k = 10) + s(TOL_5000, k = 10) 
              + s(TOL_20000, k = 10),
              data = allDrifts, family = binomial, method = "REML")

# Soundscape metrics only, GLM
model4GLM <- glm(BWpresence ~ BB_20.24000 + TOL_63 + TOL_125 + TOL_2000
              + TOL_5000 + TOL_20000,
              data = allDrifts, family = binomial)

model125 <- gam(BWpresence ~ s(TOL_125, k = 10),
              data = allDrifts, family = binomial, method = "REML")
plot(model125, trans = plogis)
summary(model125)
gam.check(model125)

# Environmental var only
model5 <- gam(BWpresence ~ s(depth) + s(mldDepth) + s(Latitude)
              + s(Longitude) + s(sst_mean) + s(curl_mean) + s(dist2slope) 
              + s(bathy_slope) + s(dist2shore) + s(chlorophyll_mean) + s(ssh_mean) 
              + s(mldTemp) + s(ttDepth) + s(ttTemp) + s(temp400) + s(sal400),
              data = allDrifts, family = binomial, method = "REML")

plogis(coef(model1[1]))
summary(model1)
summary(model4)
summary(model5)
summary(model4GLM)
plot(model4GLM)
gam.check(model1)
gam.check(model4)

#Log odds scale (when used with family = binomial)
plot(model1, pages = 6)
plot(model4, pages = 4, trans = plogis)

#Probability scale + centered on the intercept + adding intercept-related uncertainty with seWithMean arg
plot(model1, pages = 14, trans = plogis,
     shift = coef(model1)[1])#,
     #seWithMean = TRUE)

plot(model2, pages = 1, trans = plogis,
     shift = coef(model2)[1])

plot(model4, pages = 6, trans = plogis,
     shift = coef(model4)[1])
```

Top 5 environmental variables (by RF) with one drift
```{r}
# Environ only
model1 <- gam(BWpresence>0 ~ depth + sst_mean + mldTemp + ttDepth + sal400,
              data = fulltrack22, family = binomial, method = "REML")

plot(model1, trans = plogis, all.terms = TRUE)
k.check(model1)
summary(model1)
gam.check(model1)
# 16% deviance explained (buoy 7)
# 0.68% deviance explained (buoy 8)
# 8.08% deviance explained (buoy 10)
# 0.64% deviance explained (buoy 12)
# 6.94 % deviance explained (buoy 13)
# 19.5% deviance explained (buoy 14)
# 12.2% deviance explained (buoy 16)
# 8.15% deviance explained (buoy 18)
# 7.7% deviance explained (buoy 19)
# 5.5% deviance explained (buoy 20)
# 33.5% deviance explained (buoy 21)
# 13.5% deviance explained (buoy 22)
# 12.1% deviance explained (buoy 23)


# Add soundscape metrics to model 1
model2 <- gam(BWpresence>0 ~ depth + sst_mean + mldTemp + ttDepth + sal400
              + TOL_125 + TOL_2000,
              data = fulltrack22, family = binomial, method = "REML")


#plot(model2, trans = plogis) ## doesn't work
summary(model2)
gam.check(model2)
# 18.3% deviance explained (buoy 7)
# 1.25% deviance explained (buoy 8)
# 8.56% deviance explained (buoy 10)
# 1.39% deviance explained (buoy 12)
# 11.1% deviance explained (buoy 13)
# 28% deviance explained (buoy 14)
# 15% deviance explained (buoy 16)
# 9.92% deviance explained (buoy 18)
# 8.57% deviance explained (buoy 19)
# 7.3% deviance explained (buoy 20)
# 38.3% deviance explained (buoy 21)
# 15.2 % deviance explained (buoy 22)
# 20.4% deviance explained (buoy 23)
```
GAM with FULL DATASET (not great)
```{r}
alldriftGAM <- gam(BWpresence>0 ~ depth + sst_mean + mldTemp + ttDepth + sal400
              + TOL_125 + TOL_2000,
              data = allDrifts, family = binomial, method = "REML")
summary(alldriftGAM)
gam.check(alldriftGAM)
```


GAMs with s()
```{r}
# Environ only, with s()
model3 <- gam(BWpresence>0 ~ s(depth) + s(sst_mean) + s(mldTemp) + 
                s(ttDepth) + s(sal400),
              data = fulltrack21, family = binomial, method = "REML")

plot(model3, trans = plogis)
summary(model3)
gam.check(model3)
# 61.9 % deviance explained (buoy 7)
# 1.42% deviance explained (buoy 8)
# 12.5% deviance explained (buoy 10)
# 1.66% deviance explained (buoy 12)
# 12.8% deviance explained (buoy 13)
# 41.4% deviance explained (buoy 14)
# 39% deviance explained (buoy 16)
# 16.6% deviance explained (buoy 18)
# 15.5% deviance explained (buoy 19)
# 5.8% deviance explained (buoy 20)
## Iteration limit reached without full convergence -- 71.7% deviance explained (buoy 21) ???
# 18.6% deviance explained (buoy 22)
# 49.6% deviance explained (buoy 23)

#Add soundscape metrics to model 3
model4 <- gam(BWpresence>0 ~ s(depth) + s(sst_mean) + s(mldTemp) + 
                s(ttDepth) + s(sal400) + s(TOL_125) + s(TOL_2000),
              data = fulltrack10, family = binomial, method = "REML")

plot(model4, trans = plogis)
summary(model4)
gam.check(model4)
# 14.5% deviance explained

# mix and match?
model5 <- gam(BWpresence>0 ~ depth + sst_mean + s(mldTemp) + 
                s(ttDepth) + sal400,
              data = fulltrack21, family = binomial, method = "REML")

summary(model5)
gam.check(model5)
# 57.4 % deviance explained
plot(model5)


```
Higher edfs describe more wiggly curves. Doesn't mean significant
