---
title: "04_analysis"
author: "Marina Bozinovic"
date: "2023-05-11"
output: html_document
---
# Exploratory Analysis for all 13 buoys

Required Packages
```{r setup}
library(tidyverse)
```

Read in RDS files of each buoy + all environ variables + AIS
```{r}
ftlist <- dir("D:/Buoy_dfs/", recursive=TRUE, full.names=TRUE, pattern="GPSwhaleAISenvSS")

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("GPSwhaleAISenvSS", substr(ft, 29, 30)), df)
}
```

Bind ALL DRIFTS into one dataframe
```{r}
dlist <- grep(pattern = "GPSwhaleAISenvSS", names(.GlobalEnv), value = T)

# Create a new column that specifies the drift number before the bind.
for (col in dlist){
  data <- get(col) %>% mutate(Deployment = substr(col,17,18))
  data <- data[data$species %in% c(NA, "ZC", "PM", "BB", "BW43"),]    # Remove BW37V and BWC from analysis as there are too few detections.
  assign(paste0("GPSwhaleAISenvSS", substr(col,17,18)), data)
}

# Bind and save allDrifts dataframe
allDrifts <- rbind(GPSwhaleAISenvSS07, GPSwhaleAISenvSS08, GPSwhaleAISenvSS10, GPSwhaleAISenvSS12,
                   GPSwhaleAISenvSS13, GPSwhaleAISenvSS14, GPSwhaleAISenvSS16, GPSwhaleAISenvSS18,
                   GPSwhaleAISenvSS19, GPSwhaleAISenvSS20, GPSwhaleAISenvSS21, GPSwhaleAISenvSS22,
                   GPSwhaleAISenvSS23)

# Remove points where buoy is on the shelf - 300 meters
allDrifts <- allDrifts %>%
  filter(depth > 300)


save(allDrifts, file = "data/allDrifts.rda")
load(file = "data/allDrifts.rda")
```


# Which buoy was the loudest?
```{r loudest-buoy}
allDrifts %>%
  ggplot(mapping = aes(x = Deployment, y = TOL_2000)) + 
  geom_violin() + 
  geom_boxplot(width = 0.1) +
  theme_bw()

allDrifts %>%
  group_by(Deployment) %>%
  summarize(range(TOL_2000))
```

# Distribution of noise by drift
```{r}
ggplot(allDrifts, aes(x = Deployment, y = TOL_2000)) + geom_boxplot() + 
  labs(title = "Distribution of TOL2000 by Drift") +
  theme_classic()

# Where is the loudest sound level?
allDrifts[allDrifts$TOL_2000 == max(allDrifts$TOL_2000),]

# Where is the quietest sound level?
allDrifts[allDrifts$TOL_2000 == min(allDrifts$TOL_2000),]
```






### Third octave levels histograms
```{r each-drift-histogram}
# create list of fulltrack dfs from global environment to loop through
dlist <- grep(pattern = "GPSwhaleAISenvSS", names(.GlobalEnv), value = T)

# all Drifts - all TOL bands, facet wrap
for (ft in dlist) {
pivot1 <- get(ft) %>%
  pivot_longer(cols = starts_with("TOL"), names_to = "SL", values_to = "Hz")    # Pivot longer for histogram facet grid

print(ggplot(data = pivot1, aes(Hz, fill = factor(Wpresence))) +
  geom_histogram(binwidth = 1, color = "black") +
  theme_classic() +
  ggtitle(paste0("Distribution of TOL intensities: Drift", substr(ft,17,18))) +
  labs(x = "Sound Intensity (dB)") +
  guides(fill = guide_legend(title = "Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.5,0.8)) +
  (facet_grid(~factor(SL, levels = c('TOL_125', 'TOL_2000')))))
}
```

```{r all-drifts-histogram}
# Single plot for ALL DRIFTS
pivot3 <- allDrifts %>%
  # Pivot longer for histogram facet grid
  pivot_longer(cols = starts_with("TOL"), names_to = "SL", values_to = "Hz")    

ggplot(data = pivot3, aes(Hz, fill = factor(Wpresence))) +
  geom_histogram(binwidth = 2, color = "black") +
  theme_classic() +
  ggtitle("Distribution of third octave level intensities: All Drifts Combined") +
  labs(x = "Sound Intensity (dB)") +
  guides(fill = guide_legend(title = "Whale Presence")) +
  scale_fill_manual(values = c("0" = "bisque1",
                               "1" = "brown4")) +
  theme(legend.position = c(0.7,0.8)) +
  facet_grid(~factor(SL, levels = c('TOL_125', 'TOL_2000')))
```


Timeline of drifts in ocean
```{r}
ggplot(data = allDrifts, aes(x = UTC, y = Deployment)) + geom_point(aes(color = factor(Deployment)))
```

Looking at TOl2000 sound levels for each buoy and where Whale Detections happen
```{r fig.width=10}
hourly <- GPSwhaleAISenvSS10 %>% group_by(time = floor_date(UTC, '4 hours')) %>%
  summarize(mean_TOL2000 = mean(TOL_2000),
            sum_AIS = sum(shipin10km),
            sum_Wh = sum(Wpresence))

ggplot(hourly, aes(x = time, y = mean_TOL2000)) + geom_line() + 
  geom_smooth() + 
  geom_point() +
  #geom_point(aes(color = species)) +
  #geom_vline(xintercept = hourly$UTC[hourly$shipin10km == 1], color = "yellow", alpha = 0.5) +
  scale_color_discrete(na.translate=FALSE) #+
 # scale_x_datetime(date_breaks = "1 day",limits = as.POSIXct(c("2018-09-24 00:00:00", "2018-10-03 00:00:00")))
```
# Sound levels across the whole range
```{r fig.width = 10}
ggplot(allDrifts, aes(UTC,TOL_2000, color = Deployment)) + geom_smooth() 
```



# Using rollApply for ZC
```{r}
ZC_filt <- GPSwhaleAISenvSS21 %>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)

ZC_pivot <- pivot_longer(ZC_filt, cols = rollAvg_Whl:rollAvg_125, names_to = "avg", values_to = "value")

#Plot facet grid
ggplot(ZC_pivot, aes(x = UTC, y = value, color = avg)) + geom_line() +
  facet_grid(vars(avg), scales = "free") +
  scale_x_datetime(date_breaks = "1 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1),
        legend.position = "none") +
  labs(title = "Rolling Hourly Averages of ZC Detections and   
  Soundscape Metrics - Buoy 21")
```
# rollapply for vessels
```{r}
ZC_filt_ship <- GPSwhaleAISSS20.alt%>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  mutate(rollAvg_ship = zoo::rollapply(shipin10km, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)

ZC_pivot_ship <- pivot_longer(ZC_filt_ship, cols = rollAvg_Whl:rollAvg_ship, names_to = "avg", values_to = "value")

#Plot facet grid
ggplot(ZC_pivot_ship, aes(x = UTC, y = value, color = avg)) + geom_smooth() +
  facet_grid(vars(avg), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(#angle = 90, 
                                   vjust = 0.5, hjust=1)) +
  labs(title = "Rolling Hourly Averages of ZC Detections + SS Metrics + Ships -  
       Buoy 20")
```

Original data points plotted
```{r fig.width = 12}
ZC_filt <- GPSwhaleAISenvSS10 %>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  mutate(rollAvg_ship = zoo::rollapply(shipin10km, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)

ZC_pivot_reg <- pivot_longer(ZC_filt, cols = c(TOL_125,TOL_2000, Wpresence, shipin10km), names_to = "datacol", values_to = "value")

# Regular plotted detections
ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_point(size = 0.1) +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics + Ships - Buoy 10")

ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_line() +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics + Ships - Buoy 10")

```

Vessel presence vs ZC presence
```{r}
ZC_filt_ship <- GPSwhaleAISSS20.alt %>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  mutate(rollAvg_ship = zoo::rollapply(shipin10km, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)

# One plot
ggplot(ZC_filt_ship, aes(x = UTC)) +
  geom_smooth(aes(y = rollAvg_ship, color = "ship presence")) +
  geom_smooth(aes(y = rollAvg_Whl, color = "whale")) +  
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Rolling Hourly Averages of ZC Detections and Ships -  
       Buoy 20")
  

```



# rollApply on same plot for ZC
```{r}
# Read in buoy 20 without environmental variables
GPSwhaleAISSS20.alt <- readRDS("D:/Buoy_dfs/GPSwhaleAISSS20_alt.rda")

ZC_filt_a <- GPSwhaleAISSS20.alt%>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)


# Plot lines on same plot
min_first <- min(ZC_filt_a$rollAvg_Whl)
max_first <- max(ZC_filt_a$rollAvg_Whl)
min_second <- min(ZC_filt_a$rollAvg_2000)
max_second <- max(ZC_filt_a$rollAvg_2000)

# scale and shift variables calculated based on desired mins and maxes
scale = (max_second - min_second)/(max_first - min_first)
shift = min_first - min_second

# Function to scale secondary axis
scale_function <- function(x, scale, shift){
  return ((x)*scale - shift)
}

# Function to scale secondary variable values
inv_scale_function <- function(x, scale, shift){
  return ((x + shift)/scale)
}



# Plot two lines on same plot
ggplot(ZC_filt_a, aes(x = UTC)) +
  geom_line(aes(y = rollAvg_Whl, color = "ZC presence")) +
  geom_line(aes(y = inv_scale_function(rollAvg_2000, scale, shift), color = "TOL 2000")) +
  scale_x_datetime(date_breaks = "3 days") +
  scale_y_continuous(limits = c(min_first, max_first), 
                     sec.axis = sec_axis(~scale_function(., scale, shift), 
                                         name = "TOL 2000 - hourly rolling average")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Rolling Averages of ZC Detections alongside   
       Soundscape Metrics - Buoy 20")
```

```{r}
########################################
## Manual scale
scale = 2000
ggplot(ZC_filt, aes(x = UTC)) +
  geom_smooth(aes(y = rollAvg_Whl, color = "ZC presence")) +
  geom_smooth(aes(y = rollAvg_2000/scale, color = "TOL 2000")) +
  scale_x_datetime(date_breaks = "3 days") +
  scale_y_continuous(#limits = c(0.0, 0.05),
                     sec.axis = sec_axis(~.* scale, name = "TOL 2000 - hourly rolling average")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Rolling Averages of ZC Detections alongside Soundscape Metrics - Buoy 13")

```
```{r}
ggplot(ZC_filt, aes(x = UTC)) +
  geom_smooth(aes(y = rollAvg_Whl+0.25, color = "ZC presence")) #+
  geom_smooth(aes(y = rollAvg_2000, color = "TOL 2000"))
```

# Using rollApply for PM
```{r}
PM_filt <- GPSwhaleAISenvSS14 %>% 
  filter(species %in% c("PM", NA)) %>%
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA))

PM_pivot <- pivot_longer(PM_filt, cols = rollAvg_Whl:rollAvg_125, names_to = "avg", values_to = "value")

#Plot facet grid
ggplot(PM_pivot, aes(x = UTC, y = value, color = avg)) + geom_smooth() + 
  facet_grid(vars(avg), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Rolling Averages of PM Detections alongside Soundscape Metrics - Buoy 14")
```





Compare overall TOL2000sound levels when whales are absent vs. present
```{r}
ggplot(allDrifts, aes(factor(Wpresence), TOL_2000)) + geom_boxplot()
```




Scatterplots

```{r}
# SST vs TOL 2000
ggplot(data = allDrifts, aes(x = sst_mean, y = `TOL_2000`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# SST over time (strange plot)
ggplot(allDrifts, aes(x = UTC, y = sst_mean)) +
  #geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")


# Depth vs TOL 125
ggplot(data = allDrifts, aes(x = `TOL_125`, y = depth *(-1))) +
  #geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)


# Chlorophyll vs TOL 125
ggplot(data = allDrifts, aes(x = chlorophyll_mean, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# CHl over time
ggplot(allDrifts, aes(x = UTC, y = chlorophyll_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")

# Mixed Layer Depth vs TOL125 with species
ggplot(data = allDrifts, aes(x = mldDepth, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# Mixed Layer Depth over time
ggplot(allDrifts, aes(x = UTC, y = mldDepth*(-1))) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

ggplot(data = allDrifts, aes(x = `TOL_125`, y = bathy_slope)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)
  
```



Facet Grids for Env. Variables
```{r}
#Get avg daily environmental variables
means <- allDrifts %>%
  group_by(as.Date(UTC))%>%
  summarize(sst_mean = mean(sst_mean),
            dist_slope = mean(dist2slope),
            depth = mean(depth),
            slope = mean(bathy_slope),
            dist_shore = mean(dist2shore),
            chlorophyll_mean = mean(chlorophyll_mean),
            ssh_mean = mean(ssh_mean),
            mldDepth = mean(mldDepth),
            mldTemp = mean(mldTemp),
            ttDepth = mean(ttDepth),
            ttTemp = mean(ttTemp),
            temp400 = mean(temp400),
            sal400 = mean(sal400),
            curlmean = mean(curl_mean),
            Wh_presence = sum(Wpresence))
View(means)
```

```{r}
#For surface/depth variables USING DAILY MEAN VARIABLES
trackLong <- means %>%
  pivot_longer(cols = sst_mean:ssh_mean,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("sst_mean", "dist_shore", "chlorophyll_mean", "ssh_mean")) %>%
  rename(Date = `as.Date(UTC)`)

p <- ggplot(data = trackLong, aes(x = Date, y = value)) +
  geom_line()

p + facet_grid(parameter ~ ., scales = "free_y")
  

# For MLD/Thermocline variables 
trackLong2 <- allDrifts %>%
  pivot_longer(cols = mldDepth:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("mldDepth", "mldTemp", "ttDepth", "ttTemp", "temp400", "sal400")) %>%
    rename(Date = UTC) %>%
    subset(species!="?BW")

q <- ggplot(data = trackLong2, aes(x = Date, y = value)) +
  geom_line() + geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)
q + facet_grid(parameter ~ ., scales = "free_y")

# For temp400 and salinity400 variables
env.labs <- c(`sal400` = "Salinity at 400m", 
              `temp400` = "Temperature at 400m")

trackLong3 <- allDrifts %>%
  pivot_longer(cols = temp400:sal400,
               names_to="parameter",
               values_to="value") %>%
  filter(parameter %in% c("temp400", "sal400")) %>%
  rename(`Date (2018)` = UTC)

q <- ggplot(data = trackLong3, aes(x = `Date (2018)`, y = value)) +
  #geom_line() + 
  geom_point(aes(color = species)) + 
  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43", "BW" = "BW"))
q + facet_grid(parameter ~ ., scales = "free_y", labeller = as_labeller(env.labs))
```


Use as reference for similar plot (potentially??)
Co-occurrence plots of drift 8 and vessels 
```{r}
#### 09/04/18 co-occurrence of vessel and drift within 10 km
#track08_09.04 <- tracks_SS_08 %>%
#  filter(UTC >= "2018-09-04 00:00:00" & UTC <= "2018-09-05 00:00:00")

#ggplot(data = track08_09.04, aes(x = UTC, y = `TOL_125`)) +
#  geom_vline(xintercept = as.POSIXct("2018-09-04 14:13:00"), color = "yellow", linewidth = 2) +
#  geom_text(aes(as.POSIXct("2018-09-04 14:13:00"), 88, label = "Enter vessel", hjust = 1.0)) +
#  geom_vline(xintercept = as.POSIXct("2018-09-04 15:17:00"), color = "yellow", linewidth = 2) +
#  geom_text(aes(as.POSIXct("2018-09-04 15:13:00"), 87, label = "Exit vessel", hjust = -0.1)) +
#  geom_line() + 
#  geom_point(data = track08_09.04, aes(color = species, size = 2)) +
#  scale_color_discrete(na.translate=FALSE) +
#  scale_size_continuous(guide = "none") +
#  ggtitle("Sound levels during co-occurrence of Drift 8 and a vessel on 09-04-18\n(Within 7 km)") +
#  scale_y_continuous(name = "Sound Intensity (dB) at TOL 125 Hz") +
#  scale_color_discrete(na.translate=FALSE, labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```



Density Plots - Species at TOL sound levels
```{r density-plots}
# TOL 125
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_125, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 125, Drift ", substr(ft, 17, 18))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 125 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_125, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 125 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))

# TOL 2000
for (ft in dlist) {
plt <- get(ft) %>%
  filter(!is.na(species))

  print(ggplot(data = plt, aes(TOL_2000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle(paste0("TOL 2000, Drift ", substr(ft, 17, 18))) +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43")))
}

# TOL 2000 SINGLE PLOT ALL DRIFTS
allDrifts %>%
  filter(!is.na(species)) %>%
  ggplot(aes(TOL_2000, fill = species)) + 
  geom_density(alpha = 0.5) +
  ggtitle("TOL 2000 ALL Drifts Combined") +
  scale_x_continuous(name = "Sound Intensity (dB)") +
  scale_fill_discrete(labels = c("ZC" = "Cuvier's", "BW43" = "BW43"))
```


Visualize SS for buoy 20 when GPS is malfunctioning
```{r}
# Visualize where detections are missing
GPSwhaleAISenvSS20$missingGPS <-ifelse(is.na(GPSwhaleAISenvSS20$Latitude),
                                       "yes", "no")
# Need to create rollnoise column
#ggplot(GPSwhaleAISenvSS20, aes(UTC, TOL_125)) + 
#  geom_point(aes(color = missingGPS)) + geom_line(aes(y=rollnoise)) 


```



Does time elapsed affect whale presence?

Linear model
```{r}
model6 <- lm(Wpresence>0 ~ timeAfterShip, data = allDrifts)
summary(model6)
plot(model6)
```

Avg. number of hours after ship encounter?
```{r}
mean(allDrifts$timeAfterShip) / 60 / 60
```

## Soundscape before, during, after ship passage?
Elevated TOL_125 sound levels with ship presence, only slight difference with TOL_2000
```{r}
# During
ship_event <- allDrifts %>% filter(shipin10km == 1)
no_ship <- allDrifts %>% filter(shipin10km == 0)

# Plot TOL 125
ggplot(allDrifts, aes(factor(shipin10km), TOL_125)) + geom_boxplot() + labs(x = "Ship Present?")
summary(ship_event$TOL_125)
summary(no_ship$TOL_125)

# Plot TOL_2000
ggplot(allDrifts, aes(factor(shipin10km), TOL_2000)) + geom_boxplot() + labs(x = "Ship Present?")
summary(ship_event$TOL_2000)
summary(no_ship$TOL_2000)

```

How often are there detections immediately following ship passage?
```{r}
# Filter by whale detections and mutate to hrs + days after ship event
detections <- allDrifts %>% 
  filter(Wpresence == 1) %>%
  mutate(hrsAfterShip = timeAfterShip/3600) %>%
  mutate(daysAfterShip = hrsAfterShip/24)

# Plot number of days after ship event by species
ggplot(detections, aes(species, daysAfterShip)) + geom_boxplot()
summary(detections$daysAfterShip) # Avg 5.4 days after ship
```

Visualize whale detections and ship events
```{r fig.width=10}
detsOnly <- GPSwhaleAISenvSS08 %>% filter(Wpresence == 1)
shipOnly <- GPSwhaleAISenvSS08 %>% filter(shipin10km == 1)

ggplot(GPSwhaleAISenvSS08) +
  geom_bar(shipOnly, mapping = aes(x = UTC, color = "shipin10km")) +
  geom_bar(detsOnly, mapping = aes(x = UTC, color = "Wpresence")) +
  scale_x_datetime(date_breaks = "2 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

sppcolor <- factor(detsOnly$species) 

# Version 1 - too busy??
ggplot(GPSwhaleAISenvSS08) +
  geom_point(aes(x = UTC, y = TOL_125), alpha = 0.5) +
  geom_smooth(aes(x = UTC, y = TOL_125)) +
  scale_x_datetime(date_breaks = "2 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = shipOnly$UTC, color = "green", linewidth = 1) +
  geom_vline(xintercept = detsOnly$UTC, color = "purple", linewidth = 1)

# Version 2 -  Visualize sound levels when whales present by buoy
detsOnly2 <- GPSwhaleAISenvSS08 %>% filter(Wpresence == 1)
shipOnly2 <- GPSwhaleAISenvSS08 %>% filter(shipin10km == 1)
ggplot(detsOnly2) +
  geom_vline(xintercept = shipOnly2$UTC, color = "green") +  # add line for ship presence
  geom_point(aes(x = UTC, y = TOL_2000, color = species), size = 2) +
  scale_x_datetime(date_breaks = "2 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Version 3 - presence/absence sound levels
ggplot(GPSwhaleAISenvSS08) +
  geom_point(aes(x = UTC, y = TOL_125, color = factor(species))) 

  
# All buoys
detsOnly3 <- allDrifts %>% filter(Wpresence == 1)
shipOnly3 <- allDrifts %>% filter(shipin10km == 1)
ggplot(detsOnly3) +
  geom_vline(xintercept = shipOnly3$UTC, color = "green") +  # add line for ship presence
  geom_point(aes(x = UTC, y = TOL_2000, color = species), size = 2) +
  scale_x_datetime(date_breaks = "2 days") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

#Sound levels for all species
```{r}
# Sound levels for all species
ggplot(detsOnly3) + geom_violin(aes(x = species, y = TOL_125)) +
  labs(title = "TOL 125 Sound levels by Species - All Buoys") +
  theme_classic()

ggplot(detsOnly3, aes(x = species, y = TOL_2000)) + geom_violin() +
  labs(title = "TOL 2000 Sound levels by Species - All Buoys") +
  theme_classic() +
  geom_boxplot(width = 0.1)

# TOL_2000
detsOnly3 %>%
  group_by(species) %>%
  summarize(median(TOL_2000))

# Depth
ggplot(detsOnly3) + geom_boxplot(aes(x = species, y = temp400)) +
  labs(title = "Depth by Species - All Buoys") +
  theme_classic()
```


Visualize whale detections and ship events with plotPresBar
```{r}
detsOnly <- GPSwhaleAISenvSS07 %>% filter(Wpresence == 1)
shipOnly <- GPSwhaleAISenvSS07 %>% filter(shipin10km == 1)

PAMmisc::plotPresBar(detsOnly, bin = 'hour', by = "species")

PAMmisc::plotPresBar(shipOnly, bin='hour')

```

Bin time elapsed after ship event into categories and plot
```{r}
# Drift 20
example_drift20 <- GPSwhaleAISenvSS20 %>%
  .[!is.na(GPSwhaleAISenvSS20$timeAfterShip),] %>%
  mutate(timeAfterShipCat = cut(timeAfterShip, breaks = c(0, 43200, 129600, 216000, max(timeAfterShip)),
         labels = c("12 hr", "36 hr", "60 hr", "over 60 hr"))) %>%    # cuts 12, 36, 60 hrs
  filter(!is.na(species))
View(example_drift20)

# Plot
ggplot(example_drift20, aes(x=species, fill=timeAfterShipCat)) + geom_bar(position="dodge") 

ggplot(example_drift20) + geom_histogram(aes(x = timeAfterShip)) + facet_grid(species ~.)
#ggplot(example_drift10) + geom_histogram(aes(x = timeAfterShip)) + facet_grid(species ~.)
```

#Hours After Ship Event by Species
```{r}
allDrifts %>%
  group_by(Deployment) %>%
  summarize(n = sum(shipin10km))

no_na <- allDrifts %>% filter(Wpresence == 1) %>%
  mutate(HrsafterShip = timeAfterShip /3600) %>%
  mutate(DaysAfterShip = HrsafterShip / 24)

# Hours after ship event
ggplot(no_na) + geom_histogram(aes(x = HrsafterShip), bins = 60) + facet_grid(species ~.) +
  labs(title = "Hours Elapsed from Ship Event by Species - All buoys") +
  scale_x_continuous(breaks = seq(0,500, by = 50)) +
  theme_bw()

# Days after ship event
ggplot(no_na) + geom_histogram(aes(x = DaysAfterShip), bins = 60) + facet_grid(species ~.) +
  scale_x_continuous(breaks = seq(0,20, by = 1)) +
  labs(title = "Days Elapsed from Ship Event by Species - All buoys") +
  theme_bw()

no_na %>%
  drop_na(DaysAfterShip) %>%
  group_by(species) %>%
  summarize(median(DaysAfterShip))
```

Same as above with different drift
```{r}
# Drift 10

# Find index of first ship
whereShips <- GPSwhaleAISenvSS10$shipin10km > 0
firstship <- min(which(whereShips)) # Index of the first ship

# Replace with NA where index is less than index of min value
GPSwhaleAISenvSS10[1,"timeAfterShip"] = NA  # Need to make first row with a zero into NA separately
GPSwhaleAISenvSS10[2:firstship - 1, "timeAfterShip"] = NA  # then can make the rest of rows NA

example_drift10 <- GPSwhaleAISenvSS10 %>%
  .[!is.na(GPSwhaleAISenvSS10$timeAfterShip),] %>%
  mutate(timeAfterShipCat = cut(timeAfterShip, breaks = c(0, 43200, 129600, 216000, max(timeAfterShip)),
         labels = c("12 hr", "36 hr", "60 hr", "over 60 hr"))) %>%    # cuts 12, 36, 60 hrs
  filter(!is.na(species))
#View(example_drift10)

ggplot(example_drift10, aes(x=species, fill=timeAfterShipCat)) + geom_bar(position="dodge")
```

