---
title: "loud_events"
author: "Marina Bozinovic"
date: "2024-01-22"
output: html_document
---

## Label and compare before/during/after 2kHz levels above 90th percentile

Required Packages
```{r}
library(tidyverse)
```


Load data
```{r}
# Individual Drifts
ftlist <- dir("D:/Buoy_dfs/", recursive=TRUE, full.names=TRUE, pattern="GPSwhaleAISenvSS")

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("GPSwhaleAISenvSS", substr(ft, 29, 30)), df)
}

# Drift 20 has interpolated whale calls
GPSwhaleAISSS20.alt <- readRDS("D:Buoy_dfs/GPSwhaleAISSS20_alt.rda")

# Whale detections
load("D:/Whale_detections/CCES2018_BW_and_PM_Detections.rda")

# Combined drifts
load(file = "data/allDrifts.rda")
```

Create e_ for each drift (modified from original)
```{r}
# Manipulate raw whale call dataframe
EventInfo_mut <- EventInfo %>%
  mutate(lengCalls_in_min = as.numeric((EndTime-StartTime)/60)) %>% # convert duration of calls to minutes
  rename(UTC = StartTime) %>%
  subset(species %in% c(NA, "ZC", "PM")) %>%
  select(UTC,lengCalls_in_min, Deployment)

## Change Station 15 to Station 14 here. Drift 15 and 14 are the same (mix-up during fieldwork)
EventInfo_mut$Deployment[EventInfo_mut$Deployment == 15] <- 14


# Manipulate individual drift data and remove environmental variables for simplicity
e7 <- GPSwhaleAISenvSS07 %>%
  mutate(Deployment = as.numeric("07")) %>% #add Deployment to the GPSwhaleAIS objects
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e8 <- GPSwhaleAISenvSS08 %>%
  mutate(Deployment = as.numeric("08")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e10 <- GPSwhaleAISenvSS10 %>%
  mutate(Deployment = as.numeric("10")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e12 <- GPSwhaleAISenvSS12 %>%
  mutate(Deployment = as.numeric("12")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e13 <- GPSwhaleAISenvSS13 %>%
  mutate(Deployment = as.numeric("13")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e14 <- GPSwhaleAISenvSS14 %>%
  mutate(Deployment = as.numeric("14")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e16 <- GPSwhaleAISenvSS16 %>%
  mutate(Deployment = as.numeric("16")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e18 <- GPSwhaleAISenvSS18 %>%
  mutate(Deployment = as.numeric("18")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e19 <- GPSwhaleAISenvSS19 %>%
  mutate(Deployment = as.numeric("19")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)

# No need to remove columns from this one - it has no env variables associated with it
e20 <- GPSwhaleAISSS20.alt %>%
  mutate(Deployment = as.numeric("20")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-shipin10km, -timeAfterShip)

e21 <- GPSwhaleAISenvSS21 %>%
  mutate(Deployment = as.numeric("21")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e22 <- GPSwhaleAISenvSS22 %>%
  mutate(Deployment = as.numeric("22")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)
e23 <- GPSwhaleAISenvSS23 %>%
  mutate(Deployment = as.numeric("23")) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment")) %>%
  select(-sst_mean, -curl_mean, -dist2slope, -depth, -bathy_slope,
         -dist2shore, -chlorophyll_mean, -ssh_mean, -mldDepth, -ttDepth,
         -mldTemp, -ttTemp, -temp400, -sal400, -shipin10km, -timeAfterShip)


e_all <- rbind(e7,e8,e10,e12,e13,e14,e16,e18,e19,e20,e21,e22,e23) %>%
  left_join(EventInfo_mut, by = c("UTC", "Deployment"))

#Save edited dfs
save(e7, file = "data/e7.rda")
save(e8, file = "data/e8.rda")
save(e10, file = "data/e10.rda")
save(e12, file = "data/e12.rda")
save(e13, file = "data/e13.rda")
save(e14, file = "data/e14.rda")
save(e16, file = "data/e16.rda")
save(e18, file = "data/e18.rda")
save(e19, file = "data/e19.rda")
save(e20, file = "data/e20.rda")
save(e21, file = "data/e21.rda")
save(e22, file = "data/e22.rda")
save(e23, file = "data/e23.rda")
```



Find 90th percentiles
```{r}
# Find 90th percentile of buoy 7
q7 <- quantile(GPSwhaleAISenvSS07$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 8
q8 <- quantile(GPSwhaleAISenvSS08$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 10
q10 <- quantile(GPSwhaleAISenvSS10$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 12
q12 <- quantile(GPSwhaleAISenvSS12$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 13
q13 <- quantile(GPSwhaleAISenvSS13$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 14
q14 <- quantile(GPSwhaleAISenvSS14$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 16
q16 <- quantile(GPSwhaleAISenvSS16$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 18
q18 <- quantile(GPSwhaleAISenvSS18$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 19
q19 <- quantile(GPSwhaleAISenvSS19$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 20
q20 <- quantile(GPSwhaleAISSS20.alt$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 21
q21 <- quantile(GPSwhaleAISenvSS21$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 22
q22 <- quantile(GPSwhaleAISenvSS22$TOL_2000, probs = 0.90)

# Find 90th percentile of buoy 23
q23 <- quantile(GPSwhaleAISenvSS23$TOL_2000, probs = 0.90)

# Find 90th percentile of ALL BUOYS
q_all <- quantile(e_all$TOL_2000, probs = 0.90)

save(q7, file = "data/q7.rda")
save(q8, file = "data/q8.rda")
save(q10, file = "data/q10.rda")
save(q12, file = "data/q12.rda")
save(q13, file = "data/q13.rda")
save(q14, file = "data/q14.rda")
save(q16, file = "data/q16.rda")
save(q18, file = "data/q18.rda")
save(q19, file = "data/q19.rda")
save(q20, file = "data/q20.rda")
save(q21, file = "data/q21.rda")
save(q22, file = "data/q22.rda")
save(q23, file = "data/q23.rda")
```


DELETE?? For all drifts
```{r}
# create new column to categorize times when TOL2kHz is over 90th percentile
#d_all <- e_all %>%
#  filter(species %in% c("PM", "ZC", NA)) %>% # filter out species other than sperm and Cuvier's
#  mutate(BefDurAftLOUD = ifelse(TOL_2000 > q_all, "during", "bef/aft")) %>% #assign categories when TOL2kHz is above 90th percentile
#  mutate(lengCalls_in_min = ifelse(is.na(lengCalls_in_min), 0, lengCalls_in_min)) # turn NAs into zeros in duration of calls column


#fb <- e_all %>%
  # filter out species other than sperm and Cuvier's
#  filter(species %in% c("PM", "ZC", NA)) %>%
  
  #exclude first 48 hrs of every drift
#  group_by(Deployment) %>%
#  mutate(whereFirst = if_else(row_number()==1, 1, 0)) %>%
#  mutate(tmpG = cumsum(c(FALSE, as.logical(diff(whereFirst))))) %>%
#  mutate(tmp_a = c(0, diff(UTC)) * !whereFirst) %>%
#  mutate(hrsSinceStart = cumsum(tmp_a)/3600) %>% # convert to hours
#  ungroup() %>%
#  select(-c(tmp_a, tmpG, whereFirst)) %>%
  
  ##assign categories when TOL2kHz is above 90th percentile
#  mutate(BefDurAftLOUD = ifelse(TOL_2000 > q_all, 1, 0))  # if TOL_2000 > q_all, assign "during"
```

Assign_loud <- before/during/after function
```{r}
# create a function that assigns bef/dur/aft using drift (e_) and 90th percentile value for that drift (q_)

assign_loud <- function(drift, loud_value){

drift %>%
  # identify hours elapsed since start (in order to exclude first 48 later)
  arrange(UTC) %>%
  mutate(whereFirst = if_else(row_number()==1, 1, 0),
         tmpG = cumsum(c(FALSE, as.logical(diff(whereFirst)))),
         tmp_a = c(0, diff(UTC)) * !whereFirst,
         hrsSinceStart = cumsum(tmp_a)/3600) %>% # convert seconds to hours
  select(-c(tmp_a, tmpG, whereFirst)) %>%
  
  ##assign categories when TOL2kHz is above 90th percentile
  mutate(loud = ifelse(TOL_2000 > loud_value, 1, 0),
         # Find hours since last and time to "loud" event.
         tmpF = cumsum(c(FALSE, as.logical(diff(loud)))),
         tmp_af = c(0, diff(UTC)) * !loud,
         tmp_bef = as.numeric(c(diff(UTC), 0) * !loud)) %>%
  group_by(tmpF) %>%
  mutate(hrsSinceLoud = cumsum(tmp_af)/3600,
         hrsToLoud = sort(cumsum(tmp_bef), decreasing = TRUE)/3600) %>% # convert seconds to hours
  ungroup() %>%
  select(-c(tmp_af, 
            tmp_bef,
            tmpF)) %>%
  
  # label rows as before/during/after or NA to omit 
  mutate(BefDurAftLOUD = 
                
                #label "during" if loud = 1
                ifelse(.$loud == 1, "during",
                
                    #label "after" if within 12 hrs after loud event and no upcoming loud event for 12 hrs
                    ifelse(.$hrsSinceLoud <= 12 & .$hrsToLoud >= 12, "after",
                       
                       #label in-between loud event times as "during" if its within 6 hrs of last loud event
                       # and the next loud event is within 6 hours
                       ifelse(.$hrsSinceLoud < 6 & .$hrsToLoud < 6, "during",  
                         
                            #label "before" if within 12 hrs of loud event and if 12 hrs have passed since loud event
                            ifelse(.$hrsToLoud < 12 & .$hrsSinceLoud > 12, "before", NA))))) %>%
                                         
      
      #exclude first 48 hrs of every drift
      subset(., .$hrsSinceStart > 48)
}
```

Manually calculate drift 21
```{r}
labeled21 <- e21 %>%
  # identify hours elapsed since start (in order to exclude first 48 later)
  arrange(UTC) %>%
  mutate(whereFirst = if_else(row_number()==1, 1, 0),
         tmpG = cumsum(c(FALSE, as.logical(diff(whereFirst)))),
         tmp_a = c(0, diff(UTC)) * !whereFirst,
         hrsSinceStart = cumsum(tmp_a)/60) %>% # convert MIN to hours
  select(-c(tmp_a, tmpG, whereFirst)) %>%
  
  ##assign categories when TOL2kHz is above 90th percentile
  mutate(loud = ifelse(TOL_2000 > q21, 1, 0),
         # Find hours since last and time to "loud" event.
         tmpF = cumsum(c(FALSE, as.logical(diff(loud)))),
         tmp_af = c(0, diff(UTC)) * !loud,
         tmp_bef = as.numeric(c(diff(UTC), 0) * !loud)) %>%
  group_by(tmpF) %>%
  mutate(hrsSinceLoud = cumsum(tmp_af)/60,
         hrsToLoud = sort(cumsum(tmp_bef), decreasing = TRUE)/60) %>% # convert MIN to hours
  ungroup() %>%
  select(-c(tmp_af, 
            tmp_bef,
            tmpF)) %>%
  
  # label rows as before/during/after or NA to omit 
  mutate(BefDurAftLOUD = 
                
                #label "during" if loud = 1
                ifelse(.$loud == 1, "during",
                
                    #label "after" if within 12 hrs after loud event and no upcoming loud event for 12 hrs
                    ifelse(.$hrsSinceLoud < 12 & .$hrsToLoud >= 12, "after",
                       
                       #label in-between loud event times as "during" if its within 6 hrs of last loud event
                       # and the next loud event is within 6 hours
                       ifelse(.$hrsSinceLoud < 6 & .$hrsToLoud < 6, "during",  
                         
                            #label "before" if within 12 hrs of loud event and if 12 hrs have passed since loud event
                            ifelse(.$hrsToLoud < 12 & .$hrsSinceLoud > 12, "before", NA))))) %>%
                                         
      
      #exclude first 48 hrs of every drift
      subset(., .$hrsSinceStart > 48)
```


Assign_loud function for each drift
```{r}
labeled7 <- assign_loud(e7, q7)
labeled8 <- assign_loud(e8, q8)
labeled10 <- assign_loud(e10, q10)
labeled12 <- assign_loud(e12, q12)
labeled13 <- assign_loud(e13, q13)
labeled14 <- assign_loud(e14, q14)
labeled16 <- assign_loud(e16, q16)
labeled18 <- assign_loud(e18, q18)
labeled19 <- assign_loud(e19, q19)
labeled20 <- assign_loud(e20, q20)
#labeled21 <- assign_loud(e21, q21) # has zero rows because tmp_a calculates time elapsed since start in min, not sec.
# need to do manually (SEE ABOVE)
labeled22 <- assign_loud(e22, q22)
labeled23 <- assign_loud(e23, q23)

#saveRDS(labeled7, file = "data/labeled7.rda")
```

```{r}
# Example of where loud sound events occurred in time.
ggplot(labeled7) + geom_line(aes(x = UTC, y = loud)) + 
  scale_x_datetime(date_breaks = "1 day") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(labeled7) + geom_line(aes(x = UTC, y = TOL_2000)) + 
  scale_x_datetime(date_breaks = "1 day") +
  geom_hline(yintercept = q8, color = "yellow", linewidth = 1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

For reference:
Drift number and duty cycle (on/off in min)
7-2/18
8-2/18
10-2/18
12-2/18
13-2/18
14-2/18
16-2/8
18-2/4
19-2/8
20-2/8
21-2/4
22-2/8
23-2/3


Calculate hourly probability for each drift
```{r}
hourly_prob_7 <- e7 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)
#saveRDS(hourly_prob_7, file = "data/hourly_prob_7.rda")

hourly_prob_8 <- e8 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_10 <- e10 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_12 <- e12 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_13 <- e13 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_14 <- e14 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/6) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_16<- e16 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/15) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_18 <- e18 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/30) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_19 <- e19 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/15) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_20 <- e20 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/15) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_21 <- e21 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/30) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_22 <- e22 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/15) # change the divisor based on the duty cycle (active min/hr)

hourly_prob_23 <- e23 %>%
  group_by(UTC = floor_date(UTC, "1 hour")) %>%
  summarize(totalCallmin = sum(na.omit(lengCalls_in_min))) %>%
  add_column(hrProb = .$totalCallmin/40) # change the divisor based on the duty cycle (active min/hr)
```

Attach hourly probability of detection to before/during/after df and make preliminary plot
```{r}
# Join labeled_ with hourly_prob_ dfs
plt7 <- labeled7 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_7, by = join_by("UTC_round"=="UTC"))

plt8 <- labeled8 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_8, by = join_by("UTC_round"=="UTC"))

plt10 <- labeled10 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_10, by = join_by("UTC_round"=="UTC"))

plt12 <- labeled12 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_12, by = join_by("UTC_round"=="UTC"))

plt13 <- labeled13 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_13, by = join_by("UTC_round"=="UTC"))

plt14 <- labeled14 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_14, by = join_by("UTC_round"=="UTC"))

plt16 <- labeled16 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_16, by = join_by("UTC_round"=="UTC"))

plt18 <- labeled18 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_18, by = join_by("UTC_round"=="UTC"))

plt19 <- labeled19 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_19, by = join_by("UTC_round"=="UTC"))

plt20 <- labeled20 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_20, by = join_by("UTC_round"=="UTC"))

plt21 <- labeled21 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_21, by = join_by("UTC_round"=="UTC"))

plt22 <- labeled22 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_22, by = join_by("UTC_round"=="UTC"))

plt23 <- labeled23 %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_23, by = join_by("UTC_round"=="UTC"))
```

Trim events w/in individual drifts that don't follow before/during/after pattern
```{r, fig.width=13}
plt7 <- plt7[1:1717,] #remove final before/during period
plt8 <- plt8[35:3877,] # remove final "before" period and first "during" period
plt10 <- plt10[1:4086,]
plt12 <- plt12[1:2310,]
plt13 <- plt13[92:2665,]
plt14 <- plt14[59:2246,]
plt16 <- plt16[31:809,]
plt18 <- plt18[204:1369,]
plt19 <- plt19[109:1460,]
plt20 <- plt20[95:772,]
plt21 <- plt21[20:127,] # very short!
plt22 <- plt22[4:1022,]
plt23 <- plt23[87:751,]

# Bind
plt_all <- bind_rows(plt7, plt8, plt10, plt12, plt13, plt14, plt16,
                 plt18, plt19, plt20, plt21, plt22, plt23)

plt23 %>%
  distinct(UTC, .keep_all = TRUE) %>% #remove any duplicate UTC rows
  drop_na(BefDurAftLOUD) %>%
  ggplot() + geom_bar(aes(x = UTC, color = BefDurAftLOUD, fill = BefDurAftLOUD)) + 
  scale_x_datetime(date_breaks = "1 day") +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_fill_manual(values = c("red", "blue", "green")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Time Series with Loud Sound Events - Buoy 23")
```




## Boxplots of Cuvier's and Sperm whales
```{r}
# When whales are detected, which category of loudness are they in?

#Plot ZC AND PM
plt_no_zeros <- plt_all %>% 
  filter(hrProb != 0) %>% # remove zeros
  filter(species %in% c("PM", "ZC", NA)) %>%
  na.omit(BefDurAftLOUD)
  
ggplot(plt_no_zeros) + geom_boxplot(aes(x = BefDurAftLOUD, y = hrProb, fill = species)) +
  scale_x_discrete(limits = c('before', 'during', 'after')) +
  labs(title = "Hourly Probability of ZC and PM Presence Before, During,
       and After Loud Sound Event - All Buoys",
       x = "Category", y = "Hourly Probability") +
  scale_fill_discrete(labels = c("Sperm", "Cuvier's")) +
  theme_bw()

# 60 PM calls
# 196 ZC calls

```

##Testing Statistical Significance
```{r}
# Is it distributed normally? Histogram and Shapiro-Willks test to confirm.
hist(plt_no_zeros$hrProb)
shapiro.test(plt_no_zeros$hrProb)
# no -- p-value is way less than 0.05, so given data is significantly different from the normal distribution.

# Use Kruskal-Wallis test to test if hourly probability varies by period
ZC_plt_no_zeros <- plt_no_zeros %>% filter(species %in% c("ZC", NA))
kruskal.test(hrProb ~ BefDurAftLOUD, data = ZC_plt_no_zeros) #ZC only

PM_plt_no_zeros <- plt_no_zeros %>% filter(species %in% c("PM", NA))
kruskal.test(hrProb ~ BefDurAftLOUD, data = PM_plt_no_zeros) #PM only

#p-value is more than 0.05 in both, so there is no significant differences between the groups

```



DELETE?? d_all_sum
```{r}
# Group by hour and summarize minutes of calls per hour. How to incorporate back?
#d_all_sum <- d_all %>%
#  mutate(hr = floor_date(UTC, unit = "hour")) %>%
#  group_by(hr) %>%
#  summarize(tot_min = sum(lengCalls_in_min),
#            tot_dets = sum(Wpresence),
#            avg_2000 = median(TOL_2000)) %>%
#  mutate(BefDurAftLOUD = ifelse(avg_2000 > q_all, "during", "bef/aft"))

# Plot to compare animal presence during loud sound levels vs the other times.

# Loud events vs whale presence/absence for ALL DRIFTS
#ggplot(d_all, aes(Loud_event, TOL_2000)) + 
#  geom_boxplot(aes(x = as.factor(BefDurAftLOUD), y = TOL_2000, fill = as.factor(Wpresence))) +
#  guides(fill=guide_legend(title="Whale presence"))

# total whale call minutes/hr
#ggplot(d_all_sum, aes(Sum_WhaleMinPerHr, TOL_2000_median)) + 
#  geom_point(aes(x = tot_min, y = avg_2000))+
#  geom_hline(yintercept = 87.24443, color = "red")#90th percentile line

#ggplot(d_all, aes(Length_of_whl_calls_min, TOL_2000)) + 
#  geom_point(aes(x = lengCalls_in_min, y = TOL_2000))+
#  geom_hline(yintercept = 87.24443, color = "red")#90th percentile line

```


DELETE?? e_all_time
```{r}
#e_all_time <- e_all %>%
#   mutate(BefDurAftLOUD = ifelse(TOL_2000 > q_all, 1, 0)) %>%
#   arrange(Deployment, UTC) %>%
#   mutate(tmpG = cumsum(c(FALSE, as.logical(diff(BefDurAftLOUD))))) %>%
#   mutate(tmp_a = c(0, diff(UTC)) * !BefDurAftLOUD) %>%
#  mutate(tmp_b = c(diff(UTC), 0) * !BefDurAftLOUD) %>%  
#   group_by(tmpG) %>%
#   mutate(timeFromLoud = cumsum(tmp_a)) %>%
#  mutate(timeToLoud = rev(cumsum(rev(as.numeric(tmp_b))))) %>%
#   ungroup() %>%
#   select(-c(tmp_a,tmp_b, tmpG))
  
```




#####################################################################################

Playing with boundary conditions (zz)
```{r}
## Playing around with the following

zz <- e23 %>%
     #filter out species other than Cuvier's and PM
     filter(species %in% c("ZC", "PM", NA)) %>%
     
     # identify hours elapsed since start (in order to exclude first 48 later)
     arrange(UTC) %>%
     mutate(whereFirst = if_else(row_number()==1, 1, 0),
            tmpG = cumsum(c(FALSE, as.logical(diff(whereFirst)))),
            tmp_a = c(0, diff(UTC)) * !whereFirst,
            hrsSinceStart = cumsum(tmp_a)/3600) %>% # convert seconds to hours
     select(-c(tmp_a, tmpG, whereFirst)) %>%
     
     ##assign categories when TOL2kHz is above 90th percentile
     mutate(loud = ifelse(TOL_2000 > q23, 1, 0),
            # Find hours since last and time to "loud" event.
            tmpF = cumsum(c(FALSE, as.logical(diff(loud)))),
            tmp_af = c(0, diff(UTC)) * !loud,
            tmp_bef = as.double(c(diff(UTC), 0) * !loud)) %>%
     group_by(tmpF) %>%
     mutate(hrsSinceLoud = cumsum(tmp_af)/3600,
            hrsToLoud = sort(cumsum(tmp_bef), decreasing = TRUE)/3600) %>% # convert seconds to hours
     ungroup() %>%
     select(-c(tmp_af, 
               tmp_bef,
               tmpF)) %>%
    
     # label rows as before/during/after or NA to omit 
     mutate(BefDurAftLOUD = 
                
                #label "during" if loud = 1
                ifelse(.$loud == 1, "during",
                
                    #label "after" if within 12 hrs after loud event and no upcoming loud event for 12 hrs
                    ifelse(.$hrsSinceLoud < 12 & .$hrsToLoud >= 12, "after",
                       
                       #label in-between loud event times as "during" if its within 6 hrs of last loud event
                       # and the next loud event is within 6 hours
                       ifelse(.$hrsSinceLoud < 6 & .$hrsToLoud < 6, "during",  
                         
                            #label "before" if within 12 hrs of loud event and if 12 hrs have passed since loud event
                            ifelse(.$hrsToLoud < 12 & .$hrsSinceLoud > 12, "before", NA))))) %>%
                                         
      
      #exclude first 48 hrs of every drift
      subset(., .$hrsSinceStart > 48)
```


Bef/Dur/Aft Boxplot
```{r}
# Example zz plot
plt_zz <-  zz %>%
  group_by(UTC_round = floor_date(UTC, "1 hour")) %>%
  left_join(hourly_prob_23, by = join_by("UTC_round"=="UTC")) 

plt_no_zeros <- plt_zz %>% filter(hrProb != 0) %>% # remove zeros
  na.omit(BefDurAftLOUD)

ggplot(plt_no_zeros) + 
  geom_boxplot(aes(x = as.factor(BefDurAftLOUD), y = hrProb, fill = species)) +
    scale_x_discrete(limits = c('before', 'during', 'after')) + 
    labs(title = "Hourly Probability of Whale Presence Before, During,
       and After Loud Sound Event - Buoy 23")

#7 - 
#8 - 
#10 - similar to all buoys
#12 - much higher "after" probability
#13 - slightly lower "after" prob
#14 - no plot?
#16 - "after" is MUCH higher
#18 - "after has lower prob than "during". "before" is lowest
#19 - ideal! High "before", low "after"
#20 - high "during" probability
#21 - very few detections
#22 - highest prob is "before". very few non-zero prob points
#23 - highest prob is "during". very few non-zero prob points

```

Time Series. Example of where loud events and bef/after events occurred in time
```{r, fig.width=13}
# Just zz
plt_zz %>%
  distinct(UTC, .keep_all = TRUE) %>% #remove any duplicate UTC rows
  drop_na(BefDurAftLOUD) %>%
  ggplot() + geom_bar(aes(x = UTC, color = BefDurAftLOUD, fill = BefDurAftLOUD)) + 
  scale_x_datetime(date_breaks = "1 day") +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_fill_manual(values = c("red", "blue", "green")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Time Series with Loud Sound Events - Buoy 23")
```