---
title: "maps"
author: "Marina Bozinovic"
date: "2023-06-19"
output: html_document
---

### Plot maps for Powerpoint images

Set Parameters and requried packages
```{r}
library(tidyverse)
library(sf)
library(maptiles)
library(tmap)
library(tmaptools)
library(crs)
library(terra)

theme_set(theme_bw())
tmap_mode("plot")
load("data/allDrifts.rda")
```

Establish bounding box
Create map with inset box
```{r}
# Make allDrifts an sf object
allDrifts_sf <- allDrifts %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)

# Make detections only object
detsOnly_sf <- allDrifts %>% filter(Wpresence == 1) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_make_valid()

# Establish bounding box of study area
xmin <- st_bbox(allDrifts_sf)[1]
xmax <- st_bbox(allDrifts_sf)[3]
ymin <- st_bbox(allDrifts_sf)[2]
ymax <- st_bbox(allDrifts_sf)[4]

# Add 0.5 border to the extent of drifts
bnd <- st_bbox(c(xmin - 0.5, xmax + 0.5, 
           ymin - 0.5, ymax + 0.5))

#Establish basemap with GreyCanvas basemap
us_region <- st_bbox(c(xmin = -90,
            xmax = -120, 
            ymax = 48, 
            ymin = 25), crs = st_crs(4326))
usa <- get_tiles(us_region, provider = "Esri.WorldGrayCanvas", zoom = 4)

# Inset box
sg <- bb_poly(st_bbox(allDrifts_sf))
```

Plot inset map
```{r}
# try tm_tiles

inset <- tm_shape(usa) + tm_tiles() + tm_shape(sg) + tm_borders("red")
inset

# need to fix
tm_basemap(leaflet::providers$Esri.WorldGrayCanvas) + tm_shape(sg) + tm_borders("red")

```

All Drifts Map
```{r}
# Establish basemap with OceanBaseMap
allDrifts_base <- get_tiles(allDrifts_sf, provider = "Esri.OceanBasemap", zoom = 6)

# Read in US state and MX boundaries
# States boundary
bx <- st_bbox(allDrifts_sf)

states <- st_read("data/us_states_shp") %>%
  st_transform(crs = 4326) %>%
  st_crop(bnd) # crop to allDrifts extent + 0.5

mex <- st_read("data/mexico_shp") %>%
  st_transform(crs = 4326) %>%
  st_crop(bnd) # crop to allDrifts extent + 0.5

# US + Mex borders combined
west <- st_union(states,mex)

# Plot map - ERROR??
p <- tm_shape(allDrifts_base) + tm_rgb() + 
  tm_shape(states) + tm_borders() +
  tm_shape(mex) + tm_borders() +
  tm_shape(allDrifts_sf) + tm_dots()
p
```

All Drifts with Ship detections
```{r}
# With Ship detections
shipOnly <- allDrifts_sf %>% filter(shipin10km == 1)

# Plot both
p + tm_shape(shipOnly) + tm_dots(col = "yellow")
```

Read in AIS objects
```{r}
# Read in AIS_allpts
AIS_allpts <- read_csv(file = "D:/AIS/AIS_West/AIS_allpts.csv",
                       show_col_types = FALSE)

# Make sf object
AIS_allpts_sf <- AIS_allpts %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
```


AIS Map with nearshore AIS points removed
```{r}
# Create buffer and simplify lines
us_buff <- st_simplify(st_buffer(states, dist = 20000), dTolerance = 2000)
mx_buff <- st_simplify(st_buffer(mex, dist = 20000), dTolerance = 2000)
west_buff <- st_make_valid(st_union(us_buff, mx_buff))

# View west coast with buffer
tm_shape(west_buff) + tm_borders()


# Only offshore AIS points
water <- lengths(st_intersects(AIS3, west_buff)) == 0
keep <- st_make_valid(AIS3[water,]) %>%
  st_set_crs(4326)


# View with nearshore AIS points removed
tm_shape(keep) + tm_dots(col = "green") + 
  tm_shape(west_buff) + tm_borders(col = "red")+
  tm_shape(mex) + tm_borders() +
  tm_shape(states) + tm_borders() +
  tm_shape(allDrifts_sf) + tm_dots(size = 0.01) +
  tmap_options(check.and.fix = TRUE) 


```

OLD code with single day of AIS pts
```{r}
# Make a fishnet grid over AIS points
grid <- st_make_grid(bnd, n = 30) %>%
  st_set_crs(4326)
plot(grid)

# find which grid points intersect AIS points 
# and create an index to subset from
index <- which(lengths(st_intersects(grid, keep)) > 0)

# Subset the grid to make a fishnet
fishnet <- grid[index]
#plot(fishnet)

map <- fishnet |>  
  st_as_sf() |> # cast to sf
  mutate(grid_id = row_number()) |> # create unique ID
  st_join(AIS3) |> # join the AIS dataset
  group_by(grid_id) |> # group by the grid id 
  summarize(n = n_distinct(MMSI)) # summarize by unique ship ID

# Right now, n is total number of unique ships in each grid cell.
# With more points, may want to change to avg daily unique ships.

#ggplot
ggplot() + 
  geom_sf(data = map, aes(fill = n), lwd = 0.05, color = "white") +
  geom_sf(data = states) +
  geom_sf(data = mex) +
  geom_sf(data = detsOnly_sf, col = 'green', size = 0.01) +
  geom_sf(data = west_buff, col = "red", alpha = 0.05) +
  theme_minimal()

# tmap
tm_shape(map) + tm_fill(col = 'n') +
  #tm_shape(west_buff) + tm_borders(col = "red") +
  tm_shape(mex) + tm_borders() +
  tm_shape(states) + tm_borders() #+
  #tm_shape(allDrifts_sf) + tm_dots(size = 0.01)
  

  
```


Points to line loop
```{r}
# Make a fishnet grid over AIS area
# What size cells are these?
grid <- st_make_grid(bnd, cellsize = 0.4, square = FALSE) %>%
  st_set_crs(4326)

shipList <- dir("D:/AIS/AIS_West", recursive=TRUE, full.names=TRUE, pattern=".rda")

for (i in shipList) {
  p <- readRDS(i) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  group_by(MMSI) %>%
  summarize() %>%
  filter(st_geometry_type(.) == "MULTIPOINT") %>%
  st_cast("LINESTRING")
  
  z <- grid %>%
  st_as_sf() |>
  mutate(grid_id = row_number()) |>
  st_intersection(p) |> # join AIS line df
  group_by(MMSI) |> # group by AIS id 
  count()

# Grid
  m <- grid %>%
  st_as_sf() %>%
  mutate(grid_id = row_number()) %>%
  st_join(z) %>%
  group_by(grid_id) %>% # group by AIS id
  summarize(n = n_distinct(MMSI))
  
  assign(paste0("AIS_", substr(i,21,25), "_grid"), m)
  
  print(paste0("Completed", substr(i,21,25)))
}
```

Sum up all ships on all days per grid
```{r}
f <- bind_rows(AIS_08_06_grid,AIS_08_07_grid, AIS_08_08_grid, AIS_08_09_grid, 
               AIS_08_10_grid, AIS_08_11_grid, AIS_08_12_grid, AIS_08_13_grid, 
               AIS_08_14_grid, AIS_08_15_grid, AIS_08_16_grid, AIS_08_17_grid, 
               AIS_08_18_grid, AIS_08_19_grid, AIS_08_20_grid, AIS_08_21_grid, 
               AIS_08_22_grid, AIS_08_23_grid, AIS_08_24_grid, AIS_08_25_grid, 
               AIS_08_26_grid, AIS_08_27_grid, AIS_08_28_grid, AIS_08_29_grid, 
               AIS_08_30_grid, AIS_08_31_grid, AIS_09_01_grid, AIS_09_02_grid,
               AIS_09_03_grid, AIS_09_04_grid, AIS_09_05_grid, AIS_09_06_grid, 
               AIS_09_07_grid, AIS_09_08_grid, AIS_09_09_grid, AIS_09_10_grid, 
               AIS_09_11_grid, AIS_09_12_grid, AIS_09_13_grid, AIS_09_14_grid, 
               AIS_09_15_grid, AIS_09_16_grid, AIS_09_17_grid, AIS_09_18_grid, 
               AIS_09_19_grid, AIS_09_20_grid, AIS_09_21_grid, AIS_09_22_grid, 
               AIS_09_23_grid, AIS_09_24_grid, AIS_09_25_grid, AIS_09_26_grid, 
               AIS_09_27_grid, AIS_09_28_grid, AIS_09_29_grid, AIS_09_30_grid, 
               AIS_10_01_grid, AIS_10_02_grid, AIS_10_03_grid, AIS_10_04_grid, 
               AIS_10_05_grid, AIS_10_06_grid, AIS_10_07_grid, AIS_10_08_grid, 
               AIS_10_09_grid, AIS_10_10_grid, AIS_10_11_grid, AIS_10_12_grid, 
               AIS_10_13_grid, AIS_10_14_grid, AIS_10_15_grid, AIS_10_16_grid, 
               AIS_10_17_grid, AIS_10_18_grid, AIS_10_19_grid, AIS_10_20_grid, 
               AIS_10_21_grid, AIS_10_22_grid, AIS_10_23_grid, AIS_10_24_grid, 
               AIS_10_25_grid, AIS_10_26_grid, AIS_10_27_grid, AIS_10_28_grid,
               AIS_10_29_grid, AIS_10_30_grid, AIS_10_31_grid, AIS_11_01_grid, 
               AIS_11_02_grid, AIS_11_03_grid, AIS_11_04_grid, AIS_11_05_grid, 
               AIS_11_06_grid, AIS_11_07_grid, AIS_11_08_grid, AIS_11_09_grid, 
               AIS_11_10_grid, AIS_11_11_grid, AIS_11_12_grid, AIS_11_13_grid, 
               AIS_11_14_grid, AIS_11_15_grid, AIS_11_16_grid, AIS_11_17_grid, 
               AIS_11_18_grid, AIS_11_19_grid, AIS_11_20_grid, AIS_11_21_grid, 
               AIS_11_22_grid, AIS_11_23_grid, AIS_11_24_grid, AIS_11_25_grid,
               AIS_11_26_grid, AIS_11_27_grid, AIS_11_28_grid, AIS_11_29_grid, 
               AIS_11_30_grid, AIS_12_01_grid, AIS_12_02_grid) %>%
  group_by(grid_id) %>%
  summarize(total = sum(n))

saveRDS(f, file = "D:/AIS/AIS_West/AIS_grid.rda")
```

Cut out AIS on land and coastline
```{r}
# Read in AIS points
f <- readRDS(file = "D:/AIS/AIS_West/AIS_grid.rda")

# Only offshore AIS points
f_pts_intersect <- lengths(st_intersects(f, west)) == 0
AISgrd <- st_make_valid(f[f_pts_intersect,]) %>%
  st_set_crs(4326)

#What is area of these grid cells?
st_area(grid)
st_area(AISgrd)
```
Final AIS maps
```{r fig.width=10}
# ggplot
ggplot(AISgrd) + 
  geom_sf(aes(fill = total)) +
  scale_fill_viridis_c() +
  geom_sf(data = west) +
  geom_sf(data = allDrifts_sf)

# tmap
#tm_basemap(leaflet::providers$Esri.WorldTopoMap) +
  tm_shape(AISgrd) + tm_fill(fill = 'total', 
                             col = 'lightgrey', 
                             fill.legend = tm_legend("Ship Counts"),
                             fill.scale = tm_scale_continuous()) + 
  tm_shape(west) + tm_borders(col = "black", 
                              fill = "papayawhip")+
  tm_shape(detsOnly_sf) + tm_dots(size = 0.2, 
                                  legend.show = TRUE) +
  tm_layout(legend.outside = TRUE) +
  tm_grid(alpha = 0.2, 
          col = "grey") +
  tm_scalebar() +
  tm_compass(type = "arrow", 
             position = c(0.05, 0.05), 
             color.light = "blue") +
  tm_add_legend('symbol',
                fill = "black",
                labels = "Whale Detections",
                size = 0.5,
                lwd = 2) +
  tm_place_legends_right(width = 0.2) +
  tm_title("Daily Counts of Unique AIS Vessels")

```




```{r}
#Map all tracks
main <- tm_shape(allTrackbase) + tm_rgb() +
  tm_shape(trackssf) +
  tm_grid(alpha = 0.6, col = "grey") +
  tm_dots(col = "darkblue", size = 0.001, legend.show = TRUE) +
  tm_scale_bar(width = 0.3, text.size = 3, position = c(0.2, 0.03)) +
  tm_compass(type = "arrow", position = c(0.05, 0.05), color.light = "white") +
  tm_add_legend('symbol',
                type = "line",
                col = "darkblue",
                labels = "Drifting buoy tracks",
                size = 1,
                lwd = 2)

vp <- viewport(x=0.66, y=0.8, width = 0.26, height=0.4)
main
print(inset,vp=vp)


# Map all tracks - ggplot
basemap2 <- as.data.frame(allTrackbase, xy = TRUE)
#ggplot() +
#  geom_tile(data = basemap, aes(x=x, y=y, fill = "basemap")) +
#  geom_sf(data = trackssf, mapping = aes(), color = "red")


# Map tracks 08 and 10 only
tm_shape(trackBase) + tm_rgb() + 
  tm_shape(trk_TOL_08) + tm_dots(col = "red", 
                                 legend.show = TRUE) +
  tm_shape(trk_TOL_10) + tm_dots(col = "green")

# Bounding box of drift tracks on map
lon2 <- -129.04666
lon1 <- -115.78247
lat1 <- 28.21790
lat2 <- 45.09226

basemap3 <- ne_countries(scale = "medium", type = "map_units", returnclass = "sf")

# Drift tracks
ggplot(data = basemap3) +
  geom_sf(fill = "antiquewhite") +
  coord_sf(xlim = c(lon2 - 1, lon1 + 1), ylim = c(lat1 - 1, lat2 + 1), expand = FALSE) +
  theme(panel.grid.major = element_blank()) +
  geom_path(data = tracks_sf, mapping = aes(x=long,y=lat, group = factor(station)), color = "deeppink") +
  theme(panel.background = element_rect(fill = "aliceblue"), 
        axis.text = element_blank(), axis.ticks = element_blank(), 
        axis.title = element_blank())
```

Map of soundscapes
```{r}

#CCES_08 Third Octave Level
tm_shape(trackBase) + tm_rgb() + 
  tm_shape(trk_TOL_08) + 
  tm_symbols(col = "TOL_63", 
             border.lwd = NA, 
             size = 0.5, 
             n = 10) + 
  tm_layout(legend.width = 0.5, 
            legend.position = c("right","top")) + 
  tm_legend()

ggplot() + 
  geom_sf(data = trk_TOL_08, aes(color = TOL_125, size = TOL_125), show.legend = FALSE) +
  geom_sf(data = trk_TOL_10, aes(color = TOL_125, size = TOL_125)) +
  scale_x_continuous(limits = c(-130,-122)) + 
  scale_y_continuous(limits = c(35,39)) +
  scale_color_gradient(low = "navy", high = "yellow")+
  scale_size(range = c(1,12)) +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(panel.border = element_rect(fill = NA),
        axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.position = "none")
```

Map of whale detections
```{r}
# Whale detections
ggplot() +
  geom_point(data = whales8, mapping = aes(x=long, y=lat), shape = 21, color = "black", fill = "green4", size = 4) +
  geom_point(data = whales10, mapping = aes(x=long, y=lat), shape = 21, color = "black", fill = "green4", size = 4) +
  scale_x_continuous(limits = c(-130,-122)) + 
  scale_y_continuous(limits = c(35,39)) +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(panel.border = element_rect(fill = NA),
        axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank()
        )
#ggsave("Wdetect.png")


```

Map of bathymetry
```{r}
# Bathymetry
bathym <- ggplot() +
    geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`)) +
  annotation_scale(location = "bl", width_hint = 0.4) +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))


# Alternative Bathymetry (code from Ocean Tracking Network #https://www.youtube.com/watch?v=xT2F-Y9bKLk)
bgo <- getNOAA.bathy(lon1 = -122, lon2 = -130,
                     lat1 = 35, lat2= 39, resolution = 1)  # plot bounding box around drift 8 and 10
autoplot(bgo, geom = c("raster", "contour"), coast = TRUE, show.legend = FALSE) + 
  scale_fill_etopo() + #creates ggplot object
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank())

# Soundscape + bathymetry
whales08_sf <- Wsf %>%                            
  dplyr::filter(station == "8")

ggplot() +
  geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`), show.legend = FALSE) +
  #geom_contour(data = bathy_df, mapping = aes(x=x, y=y, z=gebco_bathy, linewidth = 0.1), color = "blue", linewidth = 0.01,) +
  geom_sf(data = trk_TOL_08, aes(color = TOL_125, size = TOL_125), show.legend = FALSE) +
  geom_sf(data = whales08_sf, aes(), color = "black") +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  scale_color_gradient(low = "beige", high = "hotpink") +
  scale_fill_etopo() +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))
#ggsave("soundscape.png")
```

Map of AIS
```{r}
# Plot + crop to drift area
#basemap <- ne_countries(scale = "medium", returnclass = "sf")
#ggplot() + 
#  geom_sf(aes(), basemap) +
#  geom_path(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName), #show.legend = F) + 
  #geom_point(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName)) +
#  scale_x_continuous(limits = c(min(drift$long-0.7), max(drift$long + 0.7))) + 
#  scale_y_continuous(limits = c(min(drift$lat-0.7), max(drift$lat + 0.7)))


# AIS data
ggplot() + 
  geom_path(data = AIS_sf, mapping = aes(x=LON,y=LAT, group = VesselName, linewidth = 1), show.legend = F) +
  scale_x_continuous(limits = c(-131,-121)) + 
  scale_y_continuous(limits = c(34,40)) +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA))
#ggsave("AIS.png")
```


Map of Sea Surface Temp with rerddap, Drift 8 only
```{r}
# Multi-scale Ultra-high Resolution (MUR) SST Analysis fv04.1, Global, 0.01°, 2002-present, Daily
SSTInfo <- info('jplMURSST41') 
murSST <- griddap(SSTInfo, latitude = c(35, 39), longitude = c(-122, -130), 
                  time = c("2018-08-16", "2018-10-01"), 
                  fields = 'analysed_sst') # drift 8 dates only
SST <- murSST$data

# Raster of SST
ggplot() + 
  geom_tile(data = SST, aes(x = longitude, y = latitude, fill = analysed_sst)) +
  scale_fill_gradient(low = "darkblue", high = "yellow") +
  annotation_scale(location = "br", width_hint = 0.2, plot_unit = "km") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(), 
        axis.title = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA),
        legend.position = "none")
```

Plot distance to continental slope
```{r}
ggplot() +
  geom_raster(data = bathy_df, 
              mapping = aes(x=x, y=y,
                            fill = `gebco_bathy`)) +
  geom_sf(data = tracks_SS_08, 
          mapping = aes(col = dist_slope)) +
  geom_sf(data = cont_slope) + scale_fill_continuous(high = "lightgreen", low = "blue")
  

# PLOT distance by TOL with whales
ggplot(data = tracks_SS_08, aes(x = dist_slope, y = `TOL_125`)) + 
  geom_point() + 
  geom_smooth(color = "green") +
  theme_classic()
```

Another map - need to decide if important to keep
```{r}
# Plot
oceanBase <- get_tiles(tracks_SS_08, provider="Esri.NatGeoWorldMap", crop = TRUE)
tm_shape(oceanBase) + tm_rgb() +
  tm_shape(tracks_SS_08) +  tm_symbols(col="species", size = 1) +
  tm_layout(legend.width = 0.5, 
            legend.position = c("right","top"))


#Raster base map
oceanBase <- get_tiles(tracks_SS_10, provider="Esri.NatGeoWorldMap")
tm_shape(bathy) + tm_raster() +
  tm_shape(tracks_SS_10) + 
  tm_symbols(style = "jenks") +
  tm_layout(legend.width = 0.5)
```

```{r}
# Plots for coastline and continental slope. Do I keep?
sf08 <- st_as_sf(tracks_SS_08, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
sf10 <- st_as_sf(tracks_SS_10, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
trkraster08 <- rasterize(vect(sf08), agg)
trkraster10 <- rasterize(vect(sf10), agg)

bathy_df <- as.data.frame(bathy, xy = TRUE)

# Map the coastline and cont. slope
cont <- st_as_sf(as.contour(bathy, ))
coast <- cont %>% filter(level == 0)
cont_slope <- cont %>% filter(level == -2000) #Is 2000m the correct depth for continental shelf?
cont_slope_rast <- rasterize(cont_slope, agg, field = "level")
plot(agg)
plot(cont_slope_rast, col = "red")
cont_slope_rast <- rasterize(cont_slope, agg)
plot(cont_slope_rast, col = "red")
  
ggplot() + 
  geom_sf(data = cont, col="black") + 
  geom_sf(data = coast, col = "red") +
  geom_sf(data = cont_slope, col = "purple") +
  #geom_sf(data = whales_8_10sf, mapping = aes()) +
  scale_color_gradient(low="green", high="red")
```
